### 2017-12-10 paper-tex/paper.tex
paper tex template ready

\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[CNW]{SJTU Computer Network Workshop}{December 2017}{Shanghai, China} 
\acmYear{2017}
\copyrightyear{2017}

%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\begin{document}
\title{Predicting Internet Path Dynamics and Performance with Machine Leanring}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}

\author{Zhenghui Wang}
\affiliation{%
  \institution{Shanghai Jiao Tong University}
  \city{Shanghai} 
  \state{China} 
  \postcode{200240}
}
\email{felixwzh@outlook.com}

\author{Hao Wang}
\affiliation{%
	\institution{Shanghai Jiao Tong University}
	\city{Shanghai} 
	\state{China} 
	\postcode{200240}
}
\email{?@?.com}

\author{Yuheng Zhi}
\affiliation{%
	\institution{Shanghai Jiao Tong University}
	\city{Shanghai} 
	\state{China} 
	\postcode{200240}
}
\email{?@?.com}

\author{Shukai Liu}
\affiliation{%
	\institution{Shanghai Jiao Tong University}
	\city{Shanghai} 
	\state{China} 
	\postcode{200240}
}
\email{?@?.com}

% The default list of authors is too long for headers.
\renewcommand{\shortauthors}{CN Group}

\begin{abstract}
TODO
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

%\ccsdesc[500]{Computer systems organization~Embedded systems}
%\ccsdesc[300]{Computer systems organization~Redundancy}
%\ccsdesc{Computer systems organization~Robotics}
%\ccsdesc[100]{Networks~Network reliability}

\keywords{TODO}

\maketitle

\section{Introduction}

TODO

\section{Related Works}
TODO
\subsection{Type Changes and {\itshape Special} Characters}
You can indicate italicized words or phrases in your text with the command \texttt{{\char'134}textit}; emboldening with the command \texttt{{\char'134}textbf} and typewriter-style (for instance, for computer code) with \texttt{{\char'134}texttt}.  
\subsection{Math Equations}
You may want to display math equations in three distinct styles:
inline, numbered or non-numbered display.  Each of
the three are discussed in the next sections.

\section{Methodology}
TODO
\section{Experiment}
TODO
\section{Conclusions}
TODO

\begin{acks}
TODO
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography}

\end{document}

### 2017-12-10 paper-tex/paper.tex
minor in paper, many things to do
We'd better start writing the report now

@@
 \usepackage{booktabs} % For formal tables
+\usepackage{url}
 
@@
 \begin{abstract}
-TODO
+We study the problem of predicting internet path dynamics and performance. We use \texttt{traceroute} measurement and machine learning models.
 \end{abstract}
@@
 TODO 
-
 \section{Related Works}
 TODO
-\subsection{Type Changes and {\itshape Special} Characters}
-You can indicate italicized words or phrases in your text with the command \texttt{{\char'134}textit}; emboldening with the command \texttt{{\char'134}textbf} and typewriter-style (for instance, for computer code) with \texttt{{\char'134}texttt}.
-\subsection{Math Equations}
-You may want to display math equations in three distinct styles:
-inline, numbered or non-numbered display.  Each of
-the three are discussed in the next sections.
 

### 2017-12-14 paper-tex/paper.tex
outline for paper

@@
 \usepackage{url}
-
+\newcommand{\kai}[1]{{\bf \color{blue} [[Shukai says ``#1'']]}}
+\newcommand{\heng}[1]{{\bf \color{cyan} [[Yuheng says ``#1'']]}}
+\newcommand{\hao}[1]{{\bf \color{red} [[Hao says ``#1'']]}}
+\newcommand{\hui}[1]{{\bf \color{purple} [[Zhenghui says ``#1'']]}}
 % Copyright
@@
 \maketitle
-
+\hui{I think we should focus on the process not the final result, which is also important.}
 \section{Introduction}
 
-TODO 
+1. introduce the original paper: their task, method, and dataset
+
+2. we find some drawbacks in their data. For instance, the route change times problem discussed in github. And the way they process the data.
+
+3. we try some other models to get better performance like xgboost and LSTM.
+
 \section{Related Works}
-TODO
+1. we introduce the original paper in details
 
-\section{Methodology}
-TODO
+2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}
+
+3. very briefly introduce xgboost and lstm
+
+\section{Data Analysis}
+\hui{I think this is a important part, who will take this part?}
+
+1. We can plot some figures of the statistics of data, like the distribution of the route duration and avgRTT.
+
+2. We can further discuss the relation between routes in one path or in different paths.
+
+3. Then we could discuss why the authors of the paper process the data in a wrong way
+
+4. We show our solution for data process. three ways for random forest models.
+
 \section{Experiment}
-TODO
+\subsection{Classic Models}
+We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}.
+We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.
+
+The experiments we need to conduct are as follows:
+\begin{itemize}
+
+\item 1. \textbf{K\&fix}+RF
+\item 2. \textbf{K\&update}+RF
+\item 3. \textbf{timeslot\&update}+RF
+\item 4. \textbf{origin}+RF
+\item 5. \textbf{K\&fix}+xgBoost
+\item 6. \textbf{K\&update}+xgBoost
+\item 7. \textbf{timeslot\&update}+xgBoost
+\item 8. \textbf{origin}+xgBoost
+\end{itemize}
+
+\hui{Note}We first predict the route duration instead of resLife.
+Further study on the difference between these two predicting objective could be conduct if we have time.
+Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
+
+\subsection{Deep Models}
+
+There are two kinds of input for the LSTM at each timestep, (i) one simple scalar (ii) a vector.
+The experiments we need to conduct are as follows:
+\begin{itemize}
+\item scalar input + LSTM
+\item vector input + LSTM
+\end{itemize}
+
 \section{Conclusions}

### 2017-12-14 code/model-xgb.py

@@ -35,17 +35,35 @@ dtest[3] = xgb.DMatrix(data=X_val,label=y3_val)
 # set parameters for three tasks
 param = [None]*4
 param[1] = {
-    'max_depth':3,
-    'eta':0.3,
-    'silent':1,
-    'objective':'reg:linear'
-        }
+"reg_alpha": 0.0006,
+"colsample_bytree": 0.8,
+"scale_pos_weight": 1,
+"learning_rate": 0.0175,
+"nthread": 16,
+"min_child_weight": 11,
+"n_estimators": 1000,
+"subsample": 0.8,
+"reg_lambda": 0.0049,
+"seed": 27,
+"objective":'reg:linear',
+"max_depth": 7,
+"gamma": 0.0,
+}
 param[2] = {
-    'max_depth':20,
-    'eta':0.3,
-    'silent':1,
-    'objective':'reg:linear'
-        }
+"reg_alpha": 0.0005,
+"colsample_bytree": 0.7,
+"scale_pos_weight": 1,
+"learning_rate": 0.005,
+"nthread": 8,
+"min_child_weight": 13,
+"n_estimators": 1000,
+"subsample": 0.25,
+"reg_lambda": 0.0046,
+"seed": 27,
+"objective":'reg:linear',
+"max_depth": 5,
+"gamma": 0.7,
+}
 param[3] = {
     'max_depth':10,
     'eta':0.3,
@@ -61,19 +79,19 @@ watchlist[3] = [(dtest[3],'eval'), (dtrain[3],'train')]
 num_round = 200
 
 # train for task 1
-bst1 = xgb.train(param[1], dtrain[1], num_round, watchlist[1])
+bst1 = xgb.train(param[1], dtrain[1], 1000, watchlist[1])
 
 y1_hat= bst1.predict(dtest[1])
-output_real_and_predict_data(y1_val,y1_hat,'../data/temp_result/','task1_xgb')
+output_real_and_predict_data(y1_val,y1_hat,'../data/temp_result/','task1_xgb_tuned')
 
 
-# train for task 2
-bst2 = xgb.train(param[2], dtrain[2], num_round, watchlist[2])
-y2_hat= bst2.predict(dtest[2])
-output_real_and_predict_data(y2_val,y2_hat,'../data/temp_result/','task2_xgb')
+# # train for task 2
+# bst2 = xgb.train(param[2], dtrain[2], 1000, watchlist[2])
+# y2_hat= bst2.predict(dtest[2])
[…]

### 2017-12-17 code/model-xgb.py
some results in RF&XGB

@@ -79,7 +79,7 @@ watchlist[3] = [(dtest[3],'eval'), (dtrain[3],'train')]
 num_round = 200
 
 # train for task 1
-bst1 = xgb.train(param[1], dtrain[1], 1000, watchlist[1])
+bst1 = xgb.train(param[1], dtrain[1], 100, watchlist[1])
 
 y1_hat= bst1.predict(dtest[1])
 output_real_and_predict_data(y1_val,y1_hat,'../data/temp_result/','task1_xgb_tuned')

### 2017-12-17 code/shadow-models.py

@@ -1,0 +1,218 @@
+from utils import *
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_70+30/70/',
+#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_70+30/30/',
+#         task=1,
+#         task_name='task1/data-1-task-1-7030-RF',
+#         n_estimators=10)
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_80+20/80/',
+#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_80+20/20/',
+#         task=1,
+#         task_name='task1/data-1-task-1-8020-RF',
+#         n_estimators=10)
+#
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_70+30/70/',
+#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_70+30/30/',
+#         task=1,
+#         task_name='task1/data-2-task-1-7030-RF',
+#         n_estimators=10)
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_80+20/80/',
+#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_80+20/20/',
+#         task=1,
+#         task_name='task1/data-2-task-1-8020-RF',
+#         n_estimators=10)
+#
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/70/windowsize10/',
+#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/30/windowsize10/',
+#         task=1,
+#         task_name='task1/data-3-task-1-7030-windowsize10-RF',
+#         n_estimators=10)
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/70/windowsize20/',
+#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/30/windowsize20/',
+#         task=1,
+#         task_name='task1/data-3-task-1-7030-windowsize20-RF',
+#         n_estimators=10)
+# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/70/windowsize50/',
[…]

### 2017-12-17 code/utils.py

@@ -2,7 +2,11 @@ import csv
 import matplotlib.pyplot as plt
 import numpy as np
 import matplotlib.ticker as mtick
-
+import os
+import pandas as pd
+from sklearn.ensemble import RandomForestRegressor
+from sklearn.metrics import mean_squared_error
+import xgboost as xgb
 
 def output_real_and_predict_data(y_real,y_pred,path,filename):
     """
@@ -72,3 +76,133 @@ def _draw(xData, yData, title, outputPath):
     # plt.show()
     plt.savefig(outputPath)
     plt.close()
+
+
+
+
+def get_pd_from_path(path):
+    """
+
+    :param path: the path that contains many csv files
+    :return: a pd.df that concat all the data
+    """
+    list=[]
+    in_file_list=os.listdir(path)
+    for in_file in  in_file_list:
+        # print in_file
+        try:
+            # tmp=
+            # print tmp
+            list.append(pd.read_csv(path+in_file))
+        except:
+            pass
+    # print list
+    big_pd = pd.concat(list, axis=0, join='outer', join_axes=None, ignore_index=False,
+                    keys=None, levels=None, names=None, verify_integrity=False,
+                    copy=True)
+    return big_pd
+
+def get_task_data_from_df(df,task):
+    """
+    :param df: the input data, could be train df or test df
+    :param task: the task that we want to conduct
+    :return: X, y
+    """
+    if task ==1:
+        X=df.drop(
+            ['sampleResLife'],
+            axis=1)
+        y = df.sampleResLife
+
+    elif task==2:
+        X = df.drop(
+            ['nbRouteChangesInNextSlot'],
+            axis=1)
+        y = df.nbRouteChangesInNextSlot
+    elif task==3:
+        X = df.drop(
+            [ 'nextMinRTT', 'nextavgRTT', 'nextMaxRTT', 'nextMdevRTT'],
+            axis=1)
+        y = df.nextavgRTT
+    else:
+        exit(-1)
+
+    return X,y
+
+
+def RF_task(train_path,test_path,task,task_name,n_estimators=10):
+    trainDF=get_pd_from_path(train_path)
+    testDF = get_pd_from_path(test_path)
+    train_X , train_y = get_task_data_from_df(trainDF,task)
+    test_X, test_y = get_task_data_from_df(testDF, task)
+    rf_regressor = RandomForestRegressor(n_estimators=n_estimators, n_jobs=-1)
+    rf_regressor.fit(train_X, train_y)
[…]

### 2017-12-17 code/lstm-model.py
lstm data convert

@@ -1,0 +1,58 @@
+import numpy
+import matplotlib.pyplot as plt
+from keras.models import Sequential
+from keras.layers import Dense
+from keras.layers import LSTM
+from sklearn.preprocessing import MinMaxScaler
+import numpy as np
+from math import sin, exp, pi, cos
+
+
+def create_dataset(dataset, look_back=1):
+    dataX, dataY = [], []
+    for i in range(len(dataset)-look_back):
+        a = dataset[i:(i+look_back), 0]
+        dataX.append(a)
+        dataY.append(dataset[i + look_back, 0])
+    return numpy.array(dataX), numpy.array(dataY)
+
+
+length = 500
+data_y = np.zeros([length])
+data_y[0] = 1
+data_y[1] = 1
+for i in range(length):
+    data_y[i] = 0.3 * data_y[i - 1] + 0.6 * data_y[i - 2] + 0.6 * sin(
+        pi * cos(2 * pi * i / 250)) + 0.9 * exp(-data_y[i - 1] ** 2)
+
+data_y = np.transpose([data_y])
+scaler = MinMaxScaler(feature_range=(0, 1))
+data_y = scaler.fit_transform(data_y)
+
+look_back = 1
+trainX, trainY = create_dataset(data_y, look_back)
+trainX = np.reshape(trainX, (trainX.shape[0], 1, trainX.shape[1]))
+
+model = Sequential()
+model.add(LSTM(4, input_shape=(1, look_back)))
+model.add(Dense(1))
+model.compile(loss='mean_squared_error', optimizer='adam')
+#####################################
+print trainX.shape
+print trainY.shape
+
+#####################################
+
+# model.fit(trainX, trainY, epochs=10, batch_size=1, verbose=2)
+# trainPredict = model.predict(trainX)
+# trainPredict = scaler.inverse_transform(trainPredict)
+#
+# trainPredictPlot = np.empty_like(data_y)
+# trainPredictPlot[:, :] = np.nan
+# trainPredictPlot[look_back:len(trainPredict)+look_back, :] = trainPredict
+#
+# plt.plot(scaler.inverse_transform(data_y))
+# plt.plot(trainPredictPlot)
+# plt.show()
+
+

### 2017-12-17 code/shadow-models.py

@@ -1,218 +1,227 @@
 from utils import *
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_70+30/70/',
-#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_70+30/30/',
-#         task=1,
-#         task_name='task1/data-1-task-1-7030-RF',
-#         n_estimators=10)
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_80+20/80/',
-#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/1/task1/task1_80+20/20/',
-#         task=1,
-#         task_name='task1/data-1-task-1-8020-RF',
-#         n_estimators=10)
-#
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_70+30/70/',
-#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_70+30/30/',
-#         task=1,
-#         task_name='task1/data-2-task-1-7030-RF',
-#         n_estimators=10)
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_80+20/80/',
-#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/2/task1/task1_80+20/20/',
-#         task=1,
-#         task_name='task1/data-2-task-1-8020-RF',
-#         n_estimators=10)
-#
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/70/windowsize10/',
-#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/30/windowsize10/',
-#         task=1,
-#         task_name='task1/data-3-task-1-7030-windowsize10-RF',
-#         n_estimators=10)
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/70/windowsize20/',
-#         test_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/30/windowsize20/',
-#         task=1,
-#         task_name='task1/data-3-task-1-7030-windowsize20-RF',
-#         n_estimators=10)
-# RF_task(train_path='/home/fw/Documents/CN-group-project/data/temp_data/3/task1/task1_70+30/70/windowsize50/',
[…]

### 2017-12-17 code/utils.py

@@ -131,6 +131,15 @@ def get_task_data_from_df(df,task):
 
 
 def RF_task(train_path,test_path,task,task_name,n_estimators=10):
+    """
+    train a rf model
+    :param train_path: the path of dir that contains the .csv for each path, trianing data
+    :param test_path: the path of dir that contains the .csv for each path, testing data
+    :param task: int, 1,2,3
+    :param task_name: the name of this experiment, should include the details
+    :param n_estimators: number of trees
+    :return: none
+    """
     trainDF=get_pd_from_path(train_path)
     testDF = get_pd_from_path(test_path)
     train_X , train_y = get_task_data_from_df(trainDF,task)
@@ -144,6 +153,15 @@ def RF_task(train_path,test_path,task,task_name,n_estimators=10):
 
 
 def XGB_task(train_path,test_path,task,task_name,n_estimators=10):
+    """
+    train a xgb model
+    :param train_path: the path of dir that contains the .csv for each path, trianing data
+    :param test_path: the path of dir that contains the .csv for each path, testing data
+    :param task: int, 1,2,3
+    :param task_name: the name of this experiment, should include the details
+    :param n_estimators: number of trees
+    :return: none
+    """
     trainDF=get_pd_from_path(train_path)
     testDF = get_pd_from_path(test_path)
     train_X , train_y = get_task_data_from_df(trainDF,task)
@@ -154,19 +172,19 @@ def XGB_task(train_path,test_path,task,task_name,n_estimators=10):
 
     if task==1:
         param = {
-                # "reg_alpha": 0.0,
-                # "colsample_bytree": 0.9,
-                # "scale_pos_weight": 1,
-                # "learning_rate": 0.05,
+                "reg_alpha": 0.0,
+                "colsample_bytree": 0.9,
+                "scale_pos_weight": 1,
+                "learning_rate": 0.05,
                 "nthread": 16,
-                # "min_child_weight": 5,
-                # "n_estimators": 100,
-                # "subsample": 0.7,
-                # "reg_lambda": 0.0032,
-                # "seed": 27,
+                "min_child_weight": 5,
+                "n_estimators": 100,
+                "subsample": 0.7,
+                "reg_lambda": 0.0032,
+                "seed": 27,
                 "objective":'reg:linear',
-                # "max_depth": 7,
-                # "gamma": 0.0,
+                "max_depth": 7,
+                "gamma": 0.0,
                 }
[…]

### 2017-12-18 code/utils.py
minor

@@ -224,18 +224,46 @@ def XGB_task(train_path,test_path,task,task_name,n_estimators=10):
     output_real_and_predict_data(test_y, y_hat, '../data/temp_result/', task_name)
 
 
-def get_lstm_data_from_df(df,task,time_steps):
+def get_lstm_data_from_df(train_df,test_df,task,time_steps,min_samples_for_path=5):
     """
     convert the df data structure into lstm suitable form, vector as input
-    :param df: the input data, could be train df or test df
+
+    the current process method: use the previous k trace-route as previous k time-steps,
+    and also the label of the trace-route which does not belong to the current route.
+    The mark to distinguish different route is `sampleRouteAge`, because every route
+    begins with a `sampleRouteAge`=0.
+    But one thing left is what should be fed into the `label` feature of the trace-route
+    belongs to current route?
+
+    :param train_df: the input data, train df
+    :param test_df: the input data, test df
     :param task: the task that we want to conduct
     :param time_steps: the time_steps of a sequence
-    :return: X, y, feature_dimension
+    :param min_samples_for_path: min_samples_for_path, int, default = 5
+    :return: train_lstm_X, train_lstm_y, test_lstm_X, test_lstm_y, feature_dimension
 
-    X.shape=[samples, time steps, features]
-    y.shape=[samples, time steps]
+    numpy arrays is ok
+    train_lstm_X.shape=[samples, time steps, features]
+    train_lstm_y.shape=[samples, time steps]
+    test_lstm_X.shape=[samples, time steps, features]
+    test_lstm_y.shape=[samples, time steps]
     feature_dimension = X.shape[2]
 
     """
     # fixme: what's y.shape?
-    X,y=get_task_data_from_df(df,task)
+    train_X, train_y = get_task_data_from_df(train_df,task)
+    test_X, test_y = get_task_data_from_df(test_df, task)
+
+    train_len = train_X.shape[0]
+    test_len = test_X.shape[0]
+    min_samples_for_path = 5
+
+
+    if train_len < time_steps+min_samples_for_path:
+        return None, None, None, None, None
+
+
+
+
+
+

### 2017-12-19 code/lstm-model.py
new lstm ready

@@ -6,6 +6,7 @@ from keras.layers import LSTM
 from sklearn.preprocessing import MinMaxScaler
 import numpy as np
 from math import sin, exp, pi, cos
+from utils import *
 
 
 def create_dataset(dataset, look_back=1):
@@ -33,8 +34,18 @@ look_back = 1
 trainX, trainY = create_dataset(data_y, look_back)
 trainX = np.reshape(trainX, (trainX.shape[0], 1, trainX.shape[1]))
 
+train_df = pd.read_csv("/home/fw/Documents/CN-group-project/data/temp_data/1/task3/task3_70+30/70/1.csv")
+test_df= pd.read_csv("/home/fw/Documents/CN-group-project/data/temp_data/1/task3/task3_70+30/30/1.csv")
+
+trainX,trainY,testX,testY,feature_len=get_lstm_data_from_df(train_df=train_df,test_df=test_df,task=3,time_steps=5,min_samples_for_path=5)
+# reshape input to be [samples, time steps, features]
+trainX = np.reshape(trainX, (trainX.shape[0], -1, trainX.shape[1]))
+
+print trainX
+
 model = Sequential()
-model.add(LSTM(4, input_shape=(1, look_back)))
+model.add(LSTM(128, input_shape=(feature_len, 5)))
+
 model.add(Dense(1))
 model.compile(loss='mean_squared_error', optimizer='adam')
 #####################################
@@ -43,7 +54,7 @@ print trainY.shape
 
 #####################################
 
-# model.fit(trainX, trainY, epochs=10, batch_size=1, verbose=2)
+model.fit(trainX, trainY, epochs=100, batch_size=1, verbose=2)
 # trainPredict = model.predict(trainX)
 # trainPredict = scaler.inverse_transform(trainPredict)
 #

### 2017-12-19 code/utils.py

@@ -89,14 +89,10 @@ def get_pd_from_path(path):
     list=[]
     in_file_list=os.listdir(path)
     for in_file in  in_file_list:
-        # print in_file
         try:
-            # tmp=
-            # print tmp
             list.append(pd.read_csv(path+in_file))
         except:
             pass
-    # print list
     big_pd = pd.concat(list, axis=0, join='outer', join_axes=None, ignore_index=False,
                     keys=None, levels=None, names=None, verify_integrity=False,
                     copy=True)
@@ -233,12 +229,15 @@ def get_lstm_data_from_df(train_df,test_df,task,time_steps,min_samples_for_path=
     The mark to distinguish different route is `sampleRouteAge`, because every route
     begins with a `sampleRouteAge`=0.
     But one thing left is what should be fed into the `label` feature of the trace-route
-    belongs to current route?
+    belongs to current route? For now, we just feed 0 to indicate that the trace-route
+    belongs to current route
+
+    k+1 inputs and 1 output.
 
     :param train_df: the input data, train df
     :param test_df: the input data, test df
     :param task: the task that we want to conduct
-    :param time_steps: the time_steps of a sequence
+    :param time_steps: the time_steps of a sequence, time_steps-1 for previous, and the final one for final predict
     :param min_samples_for_path: min_samples_for_path, int, default = 5
     :return: train_lstm_X, train_lstm_y, test_lstm_X, test_lstm_y, feature_dimension
 
@@ -251,19 +250,125 @@ def get_lstm_data_from_df(train_df,test_df,task,time_steps,min_samples_for_path=
 
     """
     # fixme: what's y.shape?
-    train_X, train_y = get_task_data_from_df(train_df,task)
-    test_X, test_y = get_task_data_from_df(test_df, task)
 
-    train_len = train_X.shape[0]
-    test_len = test_X.shape[0]
+    all_df = pd.concat([train_df,test_df], axis=0, join='outer', join_axes=None, ignore_index=False,
+                    keys=None, levels=None, names=None, verify_integrity=False,
+                    copy=True)
+    all_df = all_df.reset_index(drop=True)
+
+    train_X, train_y = [], []
+    test_X, test_y = [], []
+
+    train_len = train_df.shape[0]
+    test_len = test_df.shape[0]
     min_samples_for_path = 5
 
 
-    if train_len < time_steps+min_samples_for_path:
+    if train_len < time_steps + min_samples_for_path:
[…]

### 2017-12-20 paper-tex/paper.tex
add introduction and part of related work

@@
 	\section{Introduction}
+	1. introduce the original paper: their task, method, and dataset
+	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures.
+Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity.
+Thus, it is of great significant to predict Internet path dynamics and performance.
 
-1. introduce the original paper: their task, method, and dataset
+	In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
+They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
+Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
 
-2. we find some drawbacks in their data. For instance, the route change times problem discussed in github. And the way they process the data.
+	To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction.
+Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.
 
-3. we try some other models to get better performance like xgboost and LSTM.
+	The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
+	Internet measurement initiative.
+The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers.
+However, most of the paths are not periodically sampled during this week.
+And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week.
+So the dataset only contains corresponding infomation of these 2,346 paths.
+
+	We find some drawbacks in their data process.
+	The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.
+
+	\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}
+
+	And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
+Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.
 
 	\section{Related Works}
-1. we introduce the original paper in details
+	1. introduce the original paper
+	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+
+	And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.
+	For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen.
+It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.
+	And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes.
+$F_B$ features take into account the statistical properties of route changes.
+In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot.
+	And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement.
+They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
+
+	Then they study the correlation among the input features and the targets and apply  feature selection techniques to select the best features for prediction.
+When using as input the full set of 69 input features $F_A \cup F_B \cup F_C$, and perform wrapper-based feature selection on top of this full set.
+The result shows that the top important features for three targets are not necessarily the ones in corresponding $F_A,F_B$ or $F_C$.
+
+	And the authors use three different ways of selecting input features: $(i)$  use all of the 69 features to predict each target, $(ii)$ when predicting target $X$, use corresponding feature set $F_X$, $(iii)$ after wrapper-based feature selection, use the top features for each target.
+And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor differences in output results).
 
@@
 
-\begin{acks}
-TODO
-\end{acks}
-
 	\bibliographystyle{ACM-Reference-Format}

### 2017-12-20 paper-tex/paper.tex
Data analysis updated

--- 2017-12-14 paper-tex/paper.tex
@@
 \usepackage{url}
+\usepackage{graphicx}
+\usepackage{subcaption}
 \newcommand{\kai}[1]{{\bf \color{blue} [[Shukai says ``#1'']]}}
@@
 \begin{document}
-\title{Predicting Internet Path Dynamics and Performance with Machine Leanring}
+\title{Predicting Internet Path Dynamics and Performance with Machine Learning}
 %\titlenote{Produces the permission block, and
@@
 \section{Data Analysis}
-\hui{I think this is a important part, who will take this part?}
+\hui{I think this is an important part, who will take this part?}
+\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
+With careful review of the data used in the original paper, here we (a) show the authors had used the data incorrectly in the context of making \textbf{predictions} and (b) reveal the temporal properties that the original method failed to employ but perfectly fits LSTMs (long short term memory neural networks), which we later use to improve the performance.
+
+\subsection{Justification of Data Processing}
+The original paper \cite{predict} made a major mistake on data employment: they implicitly used data from the future to predict events in the future, which is not possible.
+More specifically, all of their tests on the performance of \textit{NetPerfTrace} depend on statistics calculated out of data of all time, including the data they were to predict.
+Features like \{5, 15, 25...\} percentage point of route life, for example, takes the route life of all routes during the whole week into account, including route $r_i$.
+However, these features still take part in predicting the residual life of $r_i$.
+This is just like guessing something when you knew it.
+
+In fact, a principle of making predictions is to use the data \textbf{already observed} to guess the unobserved.
+Thus, in all the experiments of this paper, we made it a hard constraint that all the features used to predict any event at, say, time $t$, only come from the raw data collected \textbf{before} $t$.
+First, we re-validated the performance of classic machine learning methods on the 3 tasks according to our justified data processing manner, in the following 3 ways: (a) use the global features (max value, min value, distribution, etc.) of the former k\% data to train the models and predict the targets of the latter (1-k)\% data, (b) use the global features to train the models and update them during the predicting procedure and (c) use data in a certain recent time-slot to calculate the global features.
+Then we train LSTMs on these data in two different ways: (a) input only a scalar, the prediction target, to the network and (b) input the prediction target and the global features as a vector.
+
+\subsection{Temporal Properties of the Data}
+We believe temporally adjacent routes and \textbf{traceroute} records of a path share some common network nodes, thus their behavior contain implicit dependencies in temporal domain.
+While the data are organized in the order of time, the original method ignored this property but regard them as independent instances, i.e., the prediction for the next time step only depends on the features of the present, but does not use information given by more previous time steps.
+This manner fails the original method to capture even the most naive temporal dependencies.
+Here we do not provide strict proofs of the temporal dependencies that lie in these routes but simply throw some light on the possibility of their existence.
+
+\begin{figure}[tp]
+	\centering
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_8}
+		\label{fig:3.1a}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_20}
+		\label{fig:3.1b}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_21}
+		\label{fig:3.1c}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_30}
+		\label{fig:3.1d}
+	\end{subfigure}
+	\caption{Temporal patterns of route life among 4 different paths.}
+	\label{fig:3.1}
+\end{figure}
+
+\begin{figure}[!htp]
+	\centering
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_8}
+		\label{fig:3.2a}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_20}
+		\label{fig:3.2b}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_21}
+		\label{fig:3.2c}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_30}
+		\label{fig:3.2d}
+	\end{subfigure}
+	\caption{Temporal patterns of the number of route changes among 4 different paths.}
+	\label{fig:3.2}
+\end{figure}
+
+\begin{figure}[!htp]
+	\centering
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_8}
+		\label{fig:3.3a}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_20}
+		\label{fig:3.3b}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_21}
+		\label{fig:3.3c}
+	\end{subfigure}
+	\begin{subfigure}[t]{0.4\linewidth}
+		\centering
+		\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_30}
+		\label{fig:3.3d}
+	\end{subfigure}
+	\caption{Temporal patterns of round trip time among 4 different paths.}
+	\label{fig:3.3}
+\end{figure}
+
+Applying simple differential analysis to the raw data, we found the prediction targets indeed show local temporal patterns which we can hopefully capture with LSTMs.
+Fig.~\ref{fig:3.1} to Fig.~\ref{fig:3.3} exhibit differentiated results of the three prediction targets in different paths.
+We can see that these paths behave in somehow consistent temporal patterns along their own ways but differently from each other.
+
+No more solid evidence could be provided to prove the periodicity of these patterns because \textbf{pattern} itself is hard to define.
+However, these results are already enough to make us hopeful about the performance of LSTMs, which are expert in capturing temporal dependencies, no-matter long-term ones or short-term ones.
 

### 2017-12-20 data/visualize.m

@@ -1,0 +1,13 @@
+% data = csvread('raw_data.csv', 1);
+% plot(data(2:ceil(length(data)/32)-1,11) + data(2:ceil(length(data)/32)-1,12) -data(1:ceil(length(data)/32)-2,11) - data(1:ceil(length(data)/32)-2,12))
+% plot(data(ceil(length(data)/32):ceil(2*length(data)/32)-1,11) + data(ceil(length(data)/32):ceil(2*length(data)/32)-1,12) -data(ceil(length(data)/32)-1:ceil(2*length(data)/32)-2,11) - data(ceil(length(data)/32)-1:ceil(length(data)/32)-2,12))
+function visualize(idx, task)
+    data = csvread(['seperatePaths/',int2str(idx),'.csv'],1);
+    n = size(data, 1);
+    if task == 1
+        plot(data(2:n,11) + data(2:n,12) - data(1:n-1,11) - data(1:n-1,12))
+    elseif task == 2
+        plot(data(2:n,24) - data(1:n-1,24))
+    elseif task == 3
+        plot(data(2:n,72) - data(1:n-1,72))
+end

### 2017-12-20 paper-tex/paper.tex

@@
 \end{document}
+=======
+\documentclass[sigconf]{acmart}
+
+\usepackage{booktabs} % For formal tables
+\usepackage{url}
+\newcommand{\kai}[1]{{\bf \color{blue} [[Shukai says ``#1'']]}}
+\newcommand{\heng}[1]{{\bf \color{cyan} [[Yuheng says ``#1'']]}}
+\newcommand{\hao}[1]{{\bf \color{red} [[Hao says ``#1'']]}}
+\newcommand{\hui}[1]{{\bf \color{purple} [[Zhenghui says ``#1'']]}}
+% Copyright
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+%\acmDOI{10.475/123_4}
+
+% ISBN
+%\acmISBN{123-4567-24-567/08/06}
+
+%Conference
+\acmConference[CNW]{SJTU Computer Network Workshop}{December 2017}{Shanghai, China} 
+\acmYear{2017}
+\copyrightyear{2017}
+
+%\acmArticle{4}
+%\acmPrice{15.00}
+
+% These commands are optional
+%\acmBooktitle{Transactions of the ACM Woodstock conference}
+%\editor{Jennifer B. Sartor}
+%\editor{Theo D'Hondt}
+%\editor{Wolfgang De Meuter}
+
+\begin{document}
+	\title{Predicting Internet Path Dynamics and Performance with Machine Leanring}
+	%\titlenote{Produces the permission block, and
+	%  copyright information}
+	%\subtitle{Extended Abstract}
+	%\subtitlenote{The full version of the author's guide is available as
+	%  \texttt{acmart.pdf} document}
+
+	\author{Zhenghui Wang}
+	\affiliation{%
+		\institution{Shanghai Jiao Tong University}
+		\city{Shanghai} 
+		\state{China} 
+		\postcode{200240}
+	}
+	\email{felixwzh@outlook.com}
+
+	\author{Hao Wang}
+	\affiliation{%
+		\institution{Shanghai Jiao Tong University}
+		\city{Shanghai} 
+		\state{China} 
+		\postcode{200240}
+	}
+	\email{?@?.com}
+
+	\author{Yuheng Zhi}
+	\affiliation{%
+		\institution{Shanghai Jiao Tong University}
+		\city{Shanghai} 
+		\state{China} 
+		\postcode{200240}
+	}
+	\email{?@?.com}
+
+	\author{Shukai Liu}
+	\affiliation{%
+		\institution{Shanghai Jiao Tong University}
+		\city{Shanghai} 
+		\state{China} 
+		\postcode{200240}
+	}
+	\email{?@?.com}
+
+	% The default list of authors is too long for headers.
+	\renewcommand{\shortauthors}{CN Group}
+
+	\begin{abstract}
+		We study the problem of predicting internet path dynamics and performance. We use \texttt{traceroute} measurement and machine learning models.
+	\end{abstract}
+
+	%
+	% The code below should be generated by the tool at
+	% http://dl.acm.org/ccs.cfm
+	% Please copy and paste the code instead of the example below. 
+	%
+	\begin{CCSXML}
+		<ccs2012>
+		<concept>
+		<concept_id>10010520.10010553.10010562</concept_id>
+		<concept_desc>Computer systems organization~Embedded systems</concept_desc>
+		<concept_significance>500</concept_significance>
+		</concept>
+		<concept>
+		<concept_id>10010520.10010575.10010755</concept_id>
+		<concept_desc>Computer systems organization~Redundancy</concept_desc>
+		<concept_significance>300</concept_significance>
+		</concept>
+		<concept>
+		<concept_id>10010520.10010553.10010554</concept_id>
+		<concept_desc>Computer systems organization~Robotics</concept_desc>
+		<concept_significance>100</concept_significance>
+		</concept>
+		<concept>
+		<concept_id>10003033.10003083.10003095</concept_id>
+		<concept_desc>Networks~Network reliability</concept_desc>
+		<concept_significance>100</concept_significance>
+		</concept>
+		</ccs2012>  
+	\end{CCSXML}
+
+	%\ccsdesc[500]{Computer systems organization~Embedded systems}
+	%\ccsdesc[300]{Computer systems organization~Redundancy}
+	%\ccsdesc{Computer systems organization~Robotics}
+	%\ccsdesc[100]{Networks~Network reliability}
+
+	\keywords{TODO}
+
+	\maketitle
+	\hui{I think we should focus on the process not the final result, which is also important.}
+	\section{Introduction}
+	1. introduce the original paper: their task, method, and dataset
+	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures.
+Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity.
+Thus, it is of great significant to predict Internet path dynamics and performance.
+
+	In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
+They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
+Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+
+	To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction.
+Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.
+
+	The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
+	Internet measurement initiative.
+The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers.
+However, most of the paths are not periodically sampled during this week.
+And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week.
+So the dataset only contains corresponding infomation of these 2,346 paths.
+
+	We find some drawbacks in their data process.
+	The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.
+
+	\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}
+
+	And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
+Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.
+
+	\section{Related Works}
+	1. introduce the original paper
+	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+
+	And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.
+	For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen.
+It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.
+	And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes.
+$F_B$ features take into account the statistical properties of route changes.
+In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot.
+	And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement.
+They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
+
+	Then they study the correlation among the input features and the targets and apply  feature selection techniques to select the best features for prediction.
+When using as input the full set of 69 input features $F_A \cup F_B \cup F_C$, and perform wrapper-based feature selection on top of this full set.
+The result shows that the top important features for three targets are not necessarily the ones in corresponding $F_A,F_B$ or $F_C$.
+
+	And the authors use three different ways of selecting input features: $(i)$  use all of the 69 features to predict each target, $(ii)$ when predicting target $X$, use corresponding feature set $F_X$, $(iii)$ after wrapper-based feature selection, use the top features for each target.
+And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor differences in output results).
+
+	2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}
+
+	3. very briefly introduce xgboost and lstm
+
+	\section{Data Analysis}
+	\hui{I think this is a important part, who will take this part?}
+
+	1. We can plot some figures of the statistics of data, like the distribution of the route duration and avgRTT.
+
+	2. We can further discuss the relation between routes in one path or in different paths.
+
+	3. Then we could discuss why the authors of the paper process the data in a wrong way
+
+	4. We show our solution for data process. three ways for random forest models.
+
+	\section{Experiment}
+	\subsection{Classic Models}
+	We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}.
+We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.
+
+	The experiments we need to conduct are as follows:
+	\begin{itemize}
+
+		\item 1. \textbf{K\&fix}+RF
+		\item 2. \textbf{K\&update}+RF
+		\item 3. \textbf{timeslot\&update}+RF
+		\item 4. \textbf{origin}+RF
+		\item 5. \textbf{K\&fix}+xgBoost
+		\item 6. \textbf{K\&update}+xgBoost
+		\item 7. \textbf{timeslot\&update}+xgBoost
+		\item 8. \textbf{origin}+xgBoost
+	\end{itemize}
+
+	\hui{Note}We first predict the route duration instead of resLife.
+Further study on the difference between these two predicting objective could be conduct if we have time.
+Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
+
+	\subsection{Deep Models}
+
+	There are two kinds of input for the LSTM at each timestep, (i) one simple scalar (ii) a vector.
+	The experiments we need to conduct are as follows:
+	\begin{itemize}
+		\item scalar input + LSTM
+		\item vector input + LSTM
+	\end{itemize}
+
+	\section{Conclusions}
+	TODO
+
+	\bibliographystyle{ACM-Reference-Format}
+	\bibliography{bibliography}
+
+\end{document}

### 2017-12-20 paper-tex/paper.tex
merge

@@
   \maketitle
+
 \hui{I think we should focus on the process not the final result, which is also important.}
+
 \section{Introduction}
@@
 
-2. we find some drawbacks in their data. For instance, the route change times problem discussed in github. And the way they process the data.
+Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures.
+Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity.
+Thus, it is of great significant to predict Internet path dynamics and performance.
 
-3. we try some other models to get better performance like xgboost and LSTM.
+In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
+They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
+Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+
+To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction.
+Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.
+
+The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
+
+Internet measurement initiative.
+The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers.
+However, most of the paths are not periodically sampled during this week.
+And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week.
+So the dataset only contains corresponding infomation of these 2,346 paths.
+
+We find some drawbacks in their data process.
+
+The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.
+
+\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}
+
+And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
+Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.
 
 \section{Related Works}
-1. we introduce the original paper in details
+
+1. introduce the original paper
+
+In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+
+And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.
+
+For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen.
+It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.
+
+And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes.
+$F_B$ features take into account the statistical properties of route changes.
+In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot.
+
+And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement.
+They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
+
+Then they study the correlation among the input features and the targets and apply  feature selection techniques to select the best features for prediction.
+When using as input the full set of 69 input features $F_A \cup F_B \cup F_C$, and perform wrapper-based feature selection on top of this full set.
+The result shows that the top important features for three targets are not necessarily the ones in corresponding $F_A,F_B$ or $F_C$.
+
+And the authors use three different ways of selecting input features: $(i)$  use all of the 69 features to predict each target, $(ii)$ when predicting target $X$, use corresponding feature set $F_X$, $(iii)$ after wrapper-based feature selection, use the top features for each target.
+And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor differences in output results).
 

### 2017-12-20 paper-tex/paper.tex
add Methodology Section
lstm

@@
 
+\section{Methodology}
+\subsection{Data Processing}
+
+\subsection{LSTM Model}
+
 \section{Experiment}
@@
 
-\subsection{Deep Models}
+\subsection{LSTM Model}
 
-There are two kinds of input for the LSTM at each timestep, (i) one simple scalar (ii) a vector.
-The experiments we need to conduct are as follows:
-\begin{itemize}
-\item scalar input + LSTM
-\item vector input + LSTM
-\end{itemize}
+ As we observed above, among the 3 different \textit{window size} (10, 20, 50), \textit{window size} of 10 alway has the best performance.
+Thus, we set the timesteps for our LSTM model to be 10, either.
+We adopt two kinds of input for the LSTM at each timestep, (i) scalar (ii) vector.
+\subsubsection{Scalar Input}
+\begin{table}[t]
+	\centering
+	\begin{tabular}{lcc}
+		\toprule
+		{Target} &{$R_r(t)$} &{$avgRTT_P(t)$}\\
+		\midrule
+		\textit{LSTM-scalar-input} & 0.5264& 0.5530  \\
+		\bottomrule
+	\end{tabular}
+	\caption{ Experiment results of LSTM models with scalar input. }
+	\label{tab:lstm-scalar}
+\end{table}
 
+Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it.
+\textbf{Table \ref{tab:lstm-scalar}} shows the results.
+
+As we can see, for target $R_r(t)$, the ABC of LSTM is higher than random forest with \textit{data-1} and \textit{data-2}, but is much lower than random forest with \textit{data-3-ws10}.
+This shows empirical evidence that there are temporal locality with $R_r(t)$ of a path.
+We can infer $R_r(t)$ of a path from its recent routes better than using current features only.
+
+To the contrast, for target $avgRTT_P(t)$, the $ABC$ of LSTM is lower than random forest in all cases, which may indicates that $avgRTT_P(t)$ is less likely to have the temporal locality.
+
+For both tasks, use scalar input for LSTM cannot outperform random forest steadily.
+
+\subsubsection{Vector Input}
+In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM as random forest.
+More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
+\begin{table}[t]
+	\centering
+	\begin{tabular}{lcc}
+		\toprule
+		{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
+		\midrule
+		\textit{data-1}& 0.5374 & 0.7310 \\
+		\textit{data-2}& 0.4956& 0.7039     \\
+		\textit{data-3-ws10}& 0.7649 & 0.7521 \\
+		\textit{data-3-ws20}& 0.6513& 0.6901    \\
+		\textit{data-3-ws50}& 0.5647& 0.7074  \\
+		\bottomrule	
+	\end{tabular}
+	\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
+	\label{tab:lstm-vector}
+\end{table}
+
+In general, the results is consist with our previous observation that $R_r(t)$ has more temporal locality while $avgRTT_p(t)$ seems has few or no temporal locality.
+
+More specificly, for target $R_r(t)$, LSTM outperforms random forest in all the 5 data set with a maximum $ABC=0.7649$.
+And when fed with vector input, the LSTM has a significant lift in performance than LSTM with scalar input, which shows that high quality features can be benefit to not only classic shadow models like random forest, but also \textit{deep} models.
+
+However, when it comes to target $avgRTT_p(t)$, although LSTM does has better performance when fed with vector input rather than scalar input, its $ABC$ is still lower than random forest's.
+We believe it is because there is less temporal locality with $avgRTT_p(t)$.
+The more data you observed before, the better you can predict $avgRTT_p(t)$ in the future.
+Thus LSTM model cannot maximize its ability in predicting temporal patterns.
 \section{Conclusions}
@@
 
+	\section{Methodol}
+	\subsection{Data Processing}
+
+	\subsection{LSTM Model}
+
 	\section{Experiment}
 	\subsection{Classic Models}
+
 	We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}.

### 2017-12-20 paper-tex/paper.tex
add part4

--- 2017-12-20 paper-tex/paper.tex
@@
 They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
-Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+Their are three predict targets: $(i)$ the remaining life time of a route (i.e., the time before a route changes), $(ii)$ the number of route changes in a future timeslot, and $(iii)$ the average RTT  that the path $P$ will experience in the next \texttt{traceroute} measurement.
 
@@
 
-In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
+In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.
 
@@
 
+\section{Methodology}
+\subsection{Data Processing}
+We reprocess the data in several more rational ways, which in other words, predicting targets using the previous information only.
+And to be specific, we divide the data into two sets, namely training set and test set.
+We calculate statistical properties (global features) of paths using three different methods: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ .
+For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th method ($i$ can be either 1,2 or 3).
+And for the third method, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
+
+\subsection{LSTM Model}
+
 \section{Experiment}
-\subsection{Classic Models}
-We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}.
-We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.
+\subsection{Random Forest Model}
+In our experiment, firstly, we use the standard random forest model (the same as the original paper) with the reprocessed data.
+In practice, we set $k = 70, 80$ respectively.
+And in the third method of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
+We find that there is little difference when setting $k$ either to 70 or 80.
+Below are the results when $k = 70$.
+And we also define an evaluation metric $ABC$, which indicates the  area below the curve ($ABC\in[0,1]$).
+The closer $ABC$ is to $1$, the better prediction result it has.
+These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} and  illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $).
+\begin{figure*} [!htb] 
+	%\vspace{-4pt}  
+	\centering  
+	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-RF.jpg}  
+	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-RF.jpg} 
+\end{figure*} 
+\begin{figure*} 	
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize10-RF.jpg} 
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize20-RF.jpg}
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize50-RF.jpg}
+	%\vspace{-20pt}  
+	\caption{Relative prediction errors for $R_r(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
+	\label{fig:task1_RF}  
+	%\vspace{-10pt}  
+\end{figure*}
 
-The experiments we need to conduct are as follows:
-\begin{itemize}
+\begin{figure*} [!htb] 
+	%\vspace{-4pt}  
+	\centering  
+	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-RF.jpg}  
+	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-RF.jpg} 
+\end{figure*} 
+\begin{figure*} 	
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize10-RF.jpg} 
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize20-RF.jpg}
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize50-RF.jpg}
+	%\vspace{-20pt}  
+	\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
+	\label{fig:task3_RF}
+	%\vspace{-10pt}  
+\end{figure*}
 
-\item 1. \textbf{K\&fix}+RF
-\item 2. \textbf{K\&update}+RF
-\item 3. \textbf{timeslot\&update}+RF
-\item 4. \textbf{origin}+RF
-\item 5. \textbf{K\&fix}+xgBoost
-\item 6. \textbf{K\&update}+xgBoost
-\item 7. \textbf{timeslot\&update}+xgBoost
-\item 8. \textbf{origin}+xgBoost
-\end{itemize}
-
-\hui{Note}We first predict the route duration instead of resLife.
-Further study on the difference between these two predicting objective could be conduct if we have time.
-Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
-
+Table 1 describes the $ABC$ in each figure.
+\begin{table}[tbp]
+	\centering  % 表居中
+	\begin{tabular}{lcc} 
+		\hline
+		Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
+		$data-1$ & 0.4016    &0.8124   \\        
+		$data-2$ &0.3985 &0.8261 \\        
+		$data-3-ws10$  &0.7132 &0.8018 \\
+		$data-3-ws20$ &0.6314 &0.7910 \\
+		$data-3-ws50$ &0.5359  &0.7790 \\ \hline
+	\end{tabular}
+	\caption{The $ABC$ of curves
+		 in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
+	 \label{tab:result_RF}
+\end{table}
+From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different methods to process the data.
+They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
+However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality.
+It changes rapidly as time changes.
+And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model.
+Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing methods.
+It considers only the recent data in a relatively short time slot.
+Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
 \subsection{Deep Models}

### 2017-12-20 paper-tex/paper.tex

@@
 
+\item 1. \textbf{K\&fix}+RF
+\item 2. \textbf{K\&update}+RF
+\item 3. \textbf{timeslot\&update}+RF
+\item 4. \textbf{origin}+RF
+\item 5. \textbf{K\&fix}+xgBoost
+\item 6. \textbf{K\&update}+xgBoost
+\item 7. \textbf{timeslot\&update}+xgBoost
+\item 8. \textbf{origin}+xgBoost
+\end{itemize}
+\hui{Note}We first predict the route duration instead of resLife.
+Further study on the difference between these two predicting objective could be conduct if we have time.
+Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
+
+\subsection{LSTM Model}
+
 Table 1 describes the $ABC$ in each figure.
@@
 
-There are two kinds of input for the LSTM at each timestep, (i) one simple scalar (ii) a vector.
-The experiments we need to conduct are as follows:
-\begin{itemize}
-\item scalar input + LSTM
-\item vector input + LSTM
-\end{itemize}
+ As we observed above, among the 3 different \textit{window size} (10, 20, 50), \textit{window size} of 10 alway has the best performance.
+Thus, we set the timesteps for our LSTM model to be 10, either.
+We adopt two kinds of input for the LSTM at each timestep, (i) scalar (ii) vector.
+\subsubsection{Scalar Input}
+\begin{table}[t]
+	\centering
+	\begin{tabular}{lcc}
+		\toprule
+		{Target} &{$R_r(t)$} &{$avgRTT_P(t)$}\\
+		\midrule
+		\textit{LSTM-scalar-input} & 0.5264& 0.5530  \\
+		\bottomrule
+	\end{tabular}
+	\caption{ Experiment results of LSTM models with scalar input. }
+	\label{tab:lstm-scalar}
+\end{table}
 
+Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it.
+\textbf{Table \ref{tab:lstm-scalar}} shows the results.
+
+As we can see, for target $R_r(t)$, the ABC of LSTM is higher than random forest with \textit{data-1} and \textit{data-2}, but is much lower than random forest with \textit{data-3-ws10}.
+This shows empirical evidence that there are temporal locality with $R_r(t)$ of a path.
+We can infer $R_r(t)$ of a path from its recent routes better than using current features only.
+
+To the contrast, for target $avgRTT_P(t)$, the $ABC$ of LSTM is lower than random forest in all cases, which may indicates that $avgRTT_P(t)$ is less likely to have the temporal locality.
+
+For both tasks, use scalar input for LSTM cannot outperform random forest steadily.
+
+\subsubsection{Vector Input}
+In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM as random forest.
+More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
+\begin{table}[t]
+	\centering
+	\begin{tabular}{lcc}
+		\toprule
+		{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
+		\midrule
+		\textit{data-1}& 0.5374 & 0.7310 \\
+		\textit{data-2}& 0.4956& 0.7039     \\
+		\textit{data-3-ws10}& 0.7649 & 0.7521 \\
+		\textit{data-3-ws20}& 0.6513& 0.6901    \\
+		\textit{data-3-ws50}& 0.5647& 0.7074  \\
+		\bottomrule	
+	\end{tabular}
+	\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
+	\label{tab:lstm-vector}
+\end{table}
+
+In general, the results is consist with our previous observation that $R_r(t)$ has more temporal locality while $avgRTT_p(t)$ seems has few or no temporal locality.
+
+More specificly, for target $R_r(t)$, LSTM outperforms random forest in all the 5 data set with a maximum $ABC=0.7649$.
+And when fed with vector input, the LSTM has a significant lift in performance than LSTM with scalar input, which shows that high quality features can be benefit to not only classic shadow models like random forest, but also \textit{deep} models.
+
+However, when it comes to target $avgRTT_p(t)$, although LSTM does has better performance when fed with vector input rather than scalar input, its $ABC$ is still lower than random forest's.
+We believe it is because there is less temporal locality with $avgRTT_p(t)$.
+The more data you observed before, the better you can predict $avgRTT_p(t)$ in the future.
+Thus LSTM model cannot maximize its ability in predicting temporal patterns.
 \section{Conclusions}

### 2017-12-20 paper-tex/paper.tex
modify minor error
modifying

@@
 \section{Introduction}
-
-1. introduce the original paper: their task, method, and dataset
-
-Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures.
-Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity.
+Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures\cite{1}.
+%  V. Paxson. 1996. End-to-end Routing Behavior in the Internet. In Proceedings of the ACM SIGCOMM 1996 Conference (SIGCOMM ’96). ACM, New York, NY, USA.
+Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity\cite{2}.
+%U.
+Javed, I.
+Cunha, D.
+Cho"nes, E.
+Katz-Bassett, T.
+Anderson, and A.
+Krishnamurthy.
+2013.
+PoiRoot: Investigating the Root Cause of Interdomain Path Changes.
+In Proceedings of the ACM SIGCOMM 2013 Conference on SIGCOMM (SIGCOMM ’13).
+ACM, New York, NY, USA, 183–194.
 Thus, it is of great significant to predict Internet path dynamics and performance.
@@
 In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
-They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
+They use the recent route information of paths (route age for paths, route changes in the past, average RTT, etc) to do some predictions of paths.
 Their are three predict targets: $(i)$ the remaining life time of a route (i.e., the time before a route changes), $(ii)$ the number of route changes in a future timeslot, and $(iii)$ the average RTT  that the path $P$ will experience in the next \texttt{traceroute} measurement.
 
-To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction.
-Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.
+To achieve these goals, they introduce a $NETPerfTrace$ system, which relies on a standard random forest model for prediction.
+Moreover, they use extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.
 
-The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
-
-Internet measurement initiative.
-The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers.
+The dataset the authors provide with is a full week of Paris- \texttt{traceroute} measurements performed through the M-Lab open
+Internet measurement initiative\footnote{https://www.measurementlab.net/}.
+They observe more than 450,000 different paths sampled through Paris-\texttt{traceroute} measurements from more than 180 geo-distributed servers.
 However, most of the paths are not periodically sampled during this week.
 And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week.
-So the dataset only contains corresponding infomation of these 2,346 paths.
+So the dataset contains corresponding infomation of these 2,346 paths.
 
-We find some drawbacks in their data process.
-
-The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.
-
-\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}
-
-And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
+We find some drawbacks in their data process.(see section \ref{sec:dataAna} )And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
 Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.
@@
 \section{Data Analysis}
+ \label{sec:dataAna}
 \hui{I think this is an important part, who will take this part?}
@@
 
-\item 1. \textbf{K\&fix}+RF
-\item 2. \textbf{K\&update}+RF
-\item 3. \textbf{timeslot\&update}+RF
-\item 4. \textbf{origin}+RF
-\item 5. \textbf{K\&fix}+xgBoost
-\item 6. \textbf{K\&update}+xgBoost
-\item 7. \textbf{timeslot\&update}+xgBoost
-\item 8. \textbf{origin}+xgBoost
-\end{itemize}
 \hui{Note}We first predict the route duration instead of resLife.
@@
 \begin{table}[tbp]
-	\centering  % 表居中
+	\centering  
 	\begin{tabular}{lcc} 
@@
 %\editor{Wolfgang De Meuter}
-
-\begin{document}
-	\title{Predicting Internet Path Dynamics and Performance with Machine Leanring}
-	%\titlenote{Produces the permission block, and
-	%  copyright information}
-	%\subtitle{Extended Abstract}
-	%\subtitlenote{The full version of the author's guide is available as
-	%  \texttt{acmart.pdf} document}
-
-	\author{Zhenghui Wang}
-	\affiliation{%
-		\institution{Shanghai Jiao Tong University}
-		\city{Shanghai} 
-		\state{China} 
-		\postcode{200240}
-	}
-	\email{felixwzh@outlook.com}
-
-	\author{Hao Wang}
-	\affiliation{%
-		\institution{Shanghai Jiao Tong University}
-		\city{Shanghai} 
-		\state{China} 
-		\postcode{200240}
-	}
-	\email{?@?.com}
-
-	\author{Yuheng Zhi}
-	\affiliation{%
-		\institution{Shanghai Jiao Tong University}
-		\city{Shanghai} 
-		\state{China} 
-		\postcode{200240}
-	}
-	\email{?@?.com}
-
-	\author{Shukai Liu}
-	\affiliation{%
-		\institution{Shanghai Jiao Tong University}
-		\city{Shanghai} 
-		\state{China} 
-		\postcode{200240}
-	}
-	\email{?@?.com}
-
-	% The default list of authors is too long for headers.
-	\renewcommand{\shortauthors}{CN Group}
-
-	\begin{abstract}
-		We study the problem of predicting internet path dynamics and performance. We use \texttt{traceroute} measurement and machine learning models.
-	\end{abstract}
-
-	%
-	% The code below should be generated by the tool at
-	% http://dl.acm.org/ccs.cfm
-	% Please copy and paste the code instead of the example below. 
-	%
-	\begin{CCSXML}
-		<ccs2012>
-		<concept>
-		<concept_id>10010520.10010553.10010562</concept_id>
-		<concept_desc>Computer systems organization~Embedded systems</concept_desc>
-		<concept_significance>500</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10010520.10010575.10010755</concept_id>
-		<concept_desc>Computer systems organization~Redundancy</concept_desc>
-		<concept_significance>300</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10010520.10010553.10010554</concept_id>
-		<concept_desc>Computer systems organization~Robotics</concept_desc>
-		<concept_significance>100</concept_significance>
-		</concept>
-		<concept>
-		<concept_id>10003033.10003083.10003095</concept_id>
-		<concept_desc>Networks~Network reliability</concept_desc>
-		<concept_significance>100</concept_significance>
-		</concept>
-		</ccs2012>  
-	\end{CCSXML}
-
-	%\ccsdesc[500]{Computer systems organization~Embedded systems}
-	%\ccsdesc[300]{Computer systems organization~Redundancy}
-	%\ccsdesc{Computer systems organization~Robotics}
-	%\ccsdesc[100]{Networks~Network reliability}
-
-	\keywords{TODO}
-
-	\maketitle
-	\hui{I think we should focus on the process not the final result, which is also important.}
-	\section{Introduction}
-	1. introduce the original paper: their task, method, and dataset
-	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures.
-Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity.
-Thus, it is of great significant to predict Internet path dynamics and performance.
-
-	In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
-They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
-Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
-
-	To achieve these goals, it introduces a NETPerfTrace system, which relies on a standard random forest model for prediction.
-Moreover it uses extensive evaluation on the impact of different input features by studying the correlations between the inputs and the prediction targets, as well as target selection techniques.
-
-	The dataset it provides with is a full week of Paris \texttt{traceroute} measurements performed through the M-Lab open
-	Internet measurement initiative.
-The author observes more than 450,000 different paths sampled through Paris-traceroute measurements from more than 180 geo-distributed servers.
-However, most of the paths are not periodically sampled during this week.
-And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week.
-So the dataset only contains corresponding infomation of these 2,346 paths.
-
-	We find some drawbacks in their data process.
-	The author processes the data and calculates some statistics for the whole seven days and then use the data to get the ramdon forest model.
-
-	\hao{maybe we can put the detail discussion of their data process problems in data analysis part and delete the above sentence only leave the first one.}
-
-	And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
-Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.
-
-	\section{Related Works}
-	1. introduce the original paper
-	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
-
-	And to achieve these three targets, 69 input features are used to describe the  statistical properties of route dynamics and path latency.
-	For the first route dynamic target, the first group of 11 features,referred to as $F_A$, is chosen.
-It describes the statistical properties (average, minimum, maximum, and percentiles) of the route duration observed for each path.
-	And for the second target, the second group of 14 features, as $F_B$, are relevant to the prediction of number of route changes.
-$F_B$ features take into account the statistical properties of route changes.
-In addition to that, $F_B$ contains information about the number of route changes observed for a path so far and a binary feature indicating whether a route change occurred for a path in the current time slot.
-	And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement.
-They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
-
-	Then they study the correlation among the input features and the targets and apply  feature selection techniques to select the best features for prediction.
-When using as input the full set of 69 input features $F_A \cup F_B \cup F_C$, and perform wrapper-based feature selection on top of this full set.
-The result shows that the top important features for three targets are not necessarily the ones in corresponding $F_A,F_B$ or $F_C$.
-
-	And the authors use three different ways of selecting input features: $(i)$  use all of the 69 features to predict each target, $(ii)$ when predicting target $X$, use corresponding feature set $F_X$, $(iii)$ after wrapper-based feature selection, use the top features for each target.
-And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor differences in output results).
-
-	2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}
-
-	3. very briefly introduce xgboost and lstm
-
-	\section{Data Analysis}
-	\hui{I think this is a important part, who will take this part?}
-
-	1. We can plot some figures of the statistics of data, like the distribution of the route duration and avgRTT.
-
-	2. We can further discuss the relation between routes in one path or in different paths.
-
-	3. Then we could discuss why the authors of the paper process the data in a wrong way
-
-	4. We show our solution for data process. three ways for random forest models.
-
-	\section{Methodol}
-	\subsection{Data Processing}
-
-	\subsection{LSTM Model}
-
-	\section{Experiment}
-	\subsection{Classic Models}
-
-	We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}.
-We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.
-
-	The experiments we need to conduct are as follows:
-	\begin{itemize}
-
-		\item 1. \textbf{K\&fix}+RF
-		\item 2. \textbf{K\&update}+RF
-		\item 3. \textbf{timeslot\&update}+RF
-		\item 4. \textbf{origin}+RF
-		\item 5. \textbf{K\&fix}+xgBoost
-		\item 6. \textbf{K\&update}+xgBoost
-		\item 7. \textbf{timeslot\&update}+xgBoost
-		\item 8. \textbf{origin}+xgBoost
-	\end{itemize}
-
-	\hui{Note}We first predict the route duration instead of resLife.
-Further study on the difference between these two predicting objective could be conduct if we have time.
-Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
-
-	\subsection{Deep Models}
-
-	There are two kinds of input for the LSTM at each timestep, (i) one simple scalar (ii) a vector.
-	The experiments we need to conduct are as follows:
-	\begin{itemize}
-		\item scalar input + LSTM
-		\item vector input + LSTM
-	\end{itemize}
-
-	\section{Conclusions}
-	TODO
-
-	\bibliographystyle{ACM-Reference-Format}
-	\bibliography{bibliography}
-
-\end{document}

### 2017-12-20 paper-tex/paper.tex
Related work 2,3 updated.

--- 2017-12-20 paper-tex/paper.tex
@@
 They uses the recent route information of paths (route age for paths, route changes in past, average RTT, etc) to do some predictions of paths.
-Their are three predict targets: $(i)$ the remaining life time of a route (i.e., the time before a route changes), $(ii)$ the number of route changes in a future timeslot, and $(iii)$ the average RTT  that the path $P$ will experience in the next \texttt{traceroute} measurement.
+Their are three predict targets: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
 
@@
 
-1. introduce the original paper
+\paragraph{The Original Paper}
 
-In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.
+In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
 
@@
 
-2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}
+\paragraph{Other Applications of MLCN}
+The last 2 decades has seen emerging applications of machine learning techniques used in computer networks \cite{kwon2017survey}.
+Classic methods, such as SVM, RBM, PCA and LDA, and deep learning methods including DBN, DNN and RNN, are both applied to areas like anomaly detection, web security, traffic prediction, etc.
+A usual procedure is to use autoencoders, both deep and classic ones, for dimensionality reduction and depend on SVM and DBN as a classifier.
 
-3. very briefly introduce xgboost and lstm
+Here we mention a few representative works.
+Alom et al.
+\cite{alom2015intrusion} focus on intrusion detection system.
+Tao et al.
+\cite{tao2016big} search to build a data fusion algorithm with awareness of network security situation obtained by PCA, LDA and Fisher score.
+Lv et al.
+\cite{lv2015traffic} first develop deep learning methods in traffic flow prediction.
+Hou et al.
+\cite{hou2010malicious} aims to learn filtering rules for malicious contents automatically.
+Thottan et al.~\cite{thottan2003anomaly} are among the first to introduce self-learning methods to anomaly detection and a series of botnet detection methods follows up \cite{ranjan2014machine, singh2014big, beigi2014towards, zhao2013botnet}.
+
+\paragraph{XGBoost} XGBoost collects a series of machine learning algorithms under the Gradient Boosting framework.
+Specifically, we use the random forest library it provides, namely GBDT, as the implementation in the experiments.
+This library includes automatic hyper-parameter tuning, which saves us some labor.
+
+\paragraph{LSTM} LSTM is an improved version of the original RNN, which largely resolved the problem of gradient vanishing and explosion in original RNN and is capable of capturing multi-scale dependencies in sequential data.
+The main modification it made to the original RNN unit is to add multiplicative \textbf{gate} unit that control the proportions of information to forget/pass on to the next time step.
+Even more modern version of LSTM like BLSTM equip the model with the ability to learn from the future, but here we only use the basic LSTM to explore the time dependencies in the dataset.
 
@@
 \subsection{Data Processing}
-We reprocess the data in several more rational ways, which in other words, predicting targets using the previous information only.
-And to be specific, we divide the data into two sets, namely training set and test set.
-We calculate statistical properties (global features) of paths using three different methods: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ .
-For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th method ($i$ can be either 1,2 or 3).
-And for the third method, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
 
@@
 \section{Experiment}
-\subsection{Random Forest Model}
-In our experiment, firstly, we use the standard random forest model (the same as the original paper) with the reprocessed data.
-In practice, we set $k = 70, 80$ respectively.
-And in the third method of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
-We find that there is little difference when setting $k$ either to 70 or 80.
-Below are the results when $k = 70$.
-And we also define an evaluation metric $ABC$, which indicates the  area below the curve ($ABC\in[0,1]$).
-The closer $ABC$ is to $1$, the better prediction result it has.
-These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} and  illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $).
-\begin{figure*} [!htb] 
-	%\vspace{-4pt}  
-	\centering  
-	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-RF.jpg}  
-	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-RF.jpg} 
-\end{figure*} 
-\begin{figure*} 	
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize10-RF.jpg} 
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize20-RF.jpg}
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize50-RF.jpg}
-	%\vspace{-20pt}  
-	\caption{Relative prediction errors for $R_r(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
-	\label{fig:task1_RF}  
-	%\vspace{-10pt}  
-\end{figure*}
+\subsection{Classic Models}
+We show the experiment results of the 3 different data we obtained, namely \textbf{K\&fix},\textbf{K\&update},\textbf{timeslot\&update}.
+We need to find some difference between our 3 data processing methods and the authors', i.e.,\textbf{origin}.
 
-\begin{figure*} [!htb] 
-	%\vspace{-4pt}  
-	\centering  
-	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-RF.jpg}  
-	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-RF.jpg} 
-\end{figure*} 
-\begin{figure*} 	
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize10-RF.jpg} 
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize20-RF.jpg}
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize50-RF.jpg}
-	%\vspace{-20pt}  
-	\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
-	\label{fig:task3_RF}
-	%\vspace{-10pt}  
-\end{figure*}
+The experiments we need to conduct are as follows:
+\begin{itemize}
 
-Table 1 describes the $ABC$ in each figure.
-\begin{table}[tbp]
-	\centering  % 表居中
-	\begin{tabular}{lcc} 
-		\hline
-		Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
-		$data-1$ & 0.4016    &0.8124   \\        
-		$data-2$ &0.3985 &0.8261 \\        
-		$data-3-ws10$  &0.7132 &0.8018 \\
-		$data-3-ws20$ &0.6314 &0.7910 \\
-		$data-3-ws50$ &0.5359  &0.7790 \\ \hline
-	\end{tabular}
-	\caption{The $ABC$ of curves
-		 in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
-	 \label{tab:result_RF}
-\end{table}
-From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different methods to process the data.
-They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
-However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality.
-It changes rapidly as time changes.
-And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model.
-Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing methods.
-It considers only the recent data in a relatively short time slot.
-Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
+\item 1. \textbf{K\&fix}+RF
+\item 2. \textbf{K\&update}+RF
+\item 3. \textbf{timeslot\&update}+RF
+\item 4. \textbf{origin}+RF
+\item 5. \textbf{K\&fix}+xgBoost
+\item 6. \textbf{K\&update}+xgBoost
+\item 7. \textbf{timeslot\&update}+xgBoost
+\item 8. \textbf{origin}+xgBoost
+\end{itemize}
+
+\hui{Note}We first predict the route duration instead of resLife.
+Further study on the difference between these two predicting objective could be conduct if we have time.
+Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
+
 \subsection{Deep Models}
@@
 	\section{Related Works}
-	1. introduce the original paper
+	\subsection{the original paper}
 	In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a path (i.e., the time before a path changes), $(ii)$ the number of path changes in a future timeslot, and $(iii)$ the average RTT of a path in the next \texttt{traceroute} measurement.
@@
 
-	2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}
+	2. Other Applcations
 

### 2017-12-20 paper-tex/paper.tex
resume

--- 2017-12-20 paper-tex/paper.tex
@@
 
-In the original paper, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
+	In the original paper\cite{oripaper}, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
 They use the recent route information of paths (route age for paths, route changes in the past, average RTT, etc) to do some predictions of paths.
@@
 
-We find some drawbacks in their data process.(see section \ref{sec:dataAna} )And in our own work,firstly we reprocess the provided data in more resonable ways and use the same method (random forest) mentioned by the author to compare the results.
-Secondly, two other machine learning methods , xgboost and LSTM, are applied to get better performance.
+	We find some drawbacks in their data process.(see section \ref{sec:dataAna}) And in our own work, firstly we reprocess the provided data in more resonable ways and use the same method (random forest model) mentioned by the original paper\cite{oripaper} to compare the results.
+Secondly, another machine learning method, LSTM model, is applied to get better performance.
 
 	\section{Related Works}
-
-1. introduce the original paper
-
-In the original paper, the problem they solve is to use random forest model to predict three labels for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.
+	In the original paper\cite{oripaper}, the problem they solve is to use random forest model to predict three targets for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T(t)$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.
 
@@
 	And the authors use three different ways of selecting input features: $(i)$  use all of the 69 features to predict each target, $(ii)$ when predicting target $X$, use corresponding feature set $F_X$, $(iii)$ after wrapper-based feature selection, use the top features for each target.
-And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor differences in output results).
+And finally, what they get is the third way of choosing input features can achieve better results (though there is only minor difference in output results).
 
@@
 	\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
-With careful review of the data used in the original paper, here we (a) show the authors had used the data incorrectly in the context of making \textbf{predictions} and (b) reveal the temporal properties that the original method failed to employ but perfectly fits LSTMs (long short term memory neural networks), which we later use to improve the performance.
+	With careful review of the data used in the original paper, here we: $(i)$ show the authors had used the data incorrectly in the context of making predictions, and $(ii)$ reveal the temporal properties that the original method failed to employ but perfectly fits LSTM model (long short term memory neural networks), which we will later use to improve the performance.
+	\subsection{Justification of Data Processing}
+	The original paper \cite{oripaper} made a major mistake on data employment: they implicitly used data from the future to predict events in the future, which is not possible.
+More specifically, all of their tests on the performance of \textit{NetPerfTrace} depend on statistics calculated out of data of all time, including the data they were to predict.
+Features like percentiles of route life, for example, take the route life of all routes during the whole week into account, including route $r_i$.
+However, these features still take part in predicting the residual life of $r_i$.
+It resembles guessing something you already knew.
 
-\subsection{Justification of Data Processing}
-The original paper \cite{predict} made a major mistake on data employment: they implicitly used data from the future to predict events in the future, which is not possible.
-More specifically, all of their tests on the performance of \textit{NetPerfTrace} depend on statistics calculated out of data of all time, including the data they were to predict.
-Features like \{5, 15, 25...\} percentage point of route life, for example, takes the route life of all routes during the whole week into account, including route $r_i$.
-However, these features still take part in predicting the residual life of $r_i$.
-This is just like guessing something when you knew it.
-
-In fact, a principle of making predictions is to use the data \textbf{already observed} to guess the unobserved.
-Thus, in all the experiments of this paper, we made it a hard constraint that all the features used to predict any event at, say, time $t$, only come from the raw data collected \textbf{before} $t$.
-First, we re-validated the performance of classic machine learning methods on the 3 tasks according to our justified data processing manner, in the following 3 ways: (a) use the global features (max value, min value, distribution, etc.) of the former k\% data to train the models and predict the targets of the latter (1-k)\% data, (b) use the global features to train the models and update them during the predicting procedure and (c) use data in a certain recent time-slot to calculate the global features.
-Then we train LSTMs on these data in two different ways: (a) input only a scalar, the prediction target, to the network and (b) input the prediction target and the global features as a vector.
+	In fact, a principle of making predictions is to use the data already observed to guess the unobserved.
+Thus, in all the experiments of this paper, we made it a hard constraint that all the features used to predict any event at, say, time $t$, only come from the raw data collected before $t$.
+First, we re-validated the performance of classic machine learning method on two tasks(task 1 and task 3) according to our justified data processing manner, (The reason why we miss the task 2 is that it is not possible to reprocess data with respect to task 2 according to the raw data given by the original paper) in the following three ways: $(i)$ use the global statistical features (average, minimum, maximum, and percentiles, etc) of the former $k\%$ data to train the models and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global features to train the models and update them during the predicting procedure and $(iii)$ use data in a certain recent time-slot to calculate the global features.
+Then we train LSTMs on these data in two different ways: $(i)$ input only a scalar, the prediction target, to the network and $(ii)$ input the prediction target and the global features as a vector.
 
 	\subsection{Temporal Properties of the Data}
-We believe temporally adjacent routes and \textbf{traceroute} records of a path share some common network nodes, thus their behavior contain implicit dependencies in temporal domain.
+	We believe temporally adjacent routes and \texttt{traceroute} records of a path share some common network nodes, thus their behavior contain implicit dependencies in temporal domain.
 While the data are organized in the order of time, the original method ignored this property but regard them as independent instances, i.e., the prediction for the next time step only depends on the features of the present, but does not use information given by more previous time steps.
@@
 And to be specific, we divide the data into two sets, namely training set and test set.
-We calculate statistical properties (global features) of paths using three different methods: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ .
-For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th method ($i$ can be either 1,2 or 3).
-And for the third method, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
+We calculate statistical properties (global features) of paths using three different manners: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ .
+For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th manner ($i$ can be either 1,2 or 3).
+And for the third manner, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
 
@@
 In practice, we set $k = 70, 80$ respectively.
-And in the third method of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
+And in the third manner of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
 We find that there is little difference when setting $k$ either to 70 or 80.
@@
 		\centering  
-	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-RF.jpg}  
-	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-RF.jpg} 
+		\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-RF.pdf}  
+		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-RF.pdf} 
 	\end{figure*} 
 	\begin{figure*} 	
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize10-RF.jpg} 
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize20-RF.jpg}
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize50-RF.jpg}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize10-RF.pdf} 
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize20-RF.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-task-1-7030-windowsize50-RF.pdf}
 		%\vspace{-20pt}  
-	\caption{Relative prediction errors for $R_r(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
+		\caption{Relative prediction errors for $R_r(t)$ using three different data processing manners, and $window\ size$ for the below three figures are 10,20 and 50.}
 		\label{fig:task1_RF}  
@@
 		\centering  
-	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-RF.jpg}  
-	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-RF.jpg} 
+		\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-RF.pdf}  
+		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-RF.pdf} 
 	\end{figure*} 
 	\begin{figure*} 	
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize10-RF.jpg} 
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize20-RF.jpg}
-	\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize50-RF.jpg}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize10-RF.pdf} 
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize20-RF.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-task-3-7030-windowsize50-RF.pdf}
 		%\vspace{-20pt}  
-	\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing methods, and $window\ size$ for the below three figures are 10,20 and 50.}
+		\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing manners, and $window\ size$ for the below three figures are 10,20 and 50.}
 		\label{fig:task3_RF}
@@
 	\end{table}
-From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different methods to process the data.
+	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different manners to process the data.
 They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
@@
 And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model.
-Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing methods.
+Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing manners.
 It considers only the recent data in a relatively short time slot.

### 2017-12-20 paper-tex/paper.tex

@@
 
-	1. We can plot some figures of the statistics of data, like the distribution of the route duration and avgRTT.
-
-	2. We can further discuss the relation between routes in one path or in different paths.
-
-	3. Then we could discuss why the authors of the paper process the data in a wrong way
-
-	4. We show our solution for data process. three ways for random forest models.
-
 	\section{Methodology}

### 2017-12-20 paper-tex/paper.tex
Resume related work

@@
 
-	2. we can introduce some other machine learning methods applied in computer network scenarios. \hui{I'll take this part}
+	\paragraph{Other Applications of MLCN}
+	The last 2 decades has seen emerging applications of machine learning techniques used in computer networks \cite{kwon2017survey}.
+Classic methods, such as SVM, RBM, PCA and LDA, and deep learning methods including DBN, DNN and RNN, are both applied to areas like anomaly detection, web security, traffic prediction, etc.
+A usual procedure is to use autoencoders, both deep and classic ones, for dimensionality reduction and depend on SVM and DBN as a classifier.
 
-	3. very briefly introduce xgboost and lstm
+	Here we mention a few representative works.
+Alom et al.
+\cite{alom2015intrusion} focus on intrusion detection system.
+Tao et al.
+\cite{tao2016big} search to build a data fusion algorithm with awareness of network security situation obtained by PCA, LDA and Fisher score.
+Lv et al.
+\cite{lv2015traffic} first develop deep learning methods in traffic flow prediction.
+Hou et al.
+\cite{hou2010malicious} aims to learn filtering rules for malicious contents automatically.
+Thottan et al.~\cite{thottan2003anomaly} are among the first to introduce self-learning methods to anomaly detection and a series of botnet detection methods follows up \cite{ranjan2014machine, singh2014big, beigi2014towards, zhao2013botnet}.
+
+	\paragraph{Random Forest} Random Forest is a classical model in machine learning.
+It basically integrates a bunch of decision trees trained on different parts of the dataset, thus eliminating the risk of overfitting when a single tree is trained.
+A Random Forest makes predictions by averaging that of all the decision trees in it or by taking the majority vote in classification scenario.
+In addition, recent years have seen the development of Deep Random Forest, which employs the superior descriptive ability of deep models in the prediction process as well as maintaining the explanatory of decision tree-based models.
+
+	\paragraph{LSTM} LSTM is an improved version of the original RNN, which largely resolved the problem of gradient vanishing and explosion in original RNN and is capable of capturing multi-scale dependencies in sequential data.
+The main modification it made to the original RNN unit is to add multiplicative \textbf{gate} unit that control the proportions of information to forget/pass on to the next time step.
+Even more modern version of LSTM like BLSTM equip the model with the ability to learn from the future, but here we only use the basic LSTM to explore the time dependencies in the dataset.
 

### 2017-12-20 paper-tex/paper.tex
Figure3.1 - Figure3.3 updated

@@
 		\centering
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_8}
+			\includegraphics[width=0.95\linewidth]{fig/total_life_8}
 			\label{fig:3.1a}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_20}
+			\includegraphics[width=0.95\linewidth]{fig/total_life_20}
 			\label{fig:3.1b}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_21}
+			\includegraphics[width=0.95\linewidth]{fig/total_life_21}
 			\label{fig:3.1c}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_30}
+			\includegraphics[width=0.95\linewidth]{fig/total_life_30}
 			\label{fig:3.1d}
@@
 		\centering
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_8}
+			\includegraphics[width=0.95\linewidth]{fig/route_change_8}
 			\label{fig:3.2a}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_20}
+			\includegraphics[width=0.95\linewidth]{fig/route_change_20}
 			\label{fig:3.2b}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_21}
+			\includegraphics[width=0.95\linewidth]{fig/route_change_21}
 			\label{fig:3.2c}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_30}
+			\includegraphics[width=0.95\linewidth]{fig/route_change_30}
 			\label{fig:3.2d}
@@
 		\centering
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_8}
+			\includegraphics[width=0.95\linewidth]{fig/RTT_8}
 			\label{fig:3.3a}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_20}
+			\includegraphics[width=0.95\linewidth]{fig/RTT_20}
 			\label{fig:3.3b}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_21}
+			\includegraphics[width=0.95\linewidth]{fig/RTT_21}
 			\label{fig:3.3c}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
+		\begin{subfigure}[t]{0.45\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_30}
+			\includegraphics[width=0.95\linewidth]{fig/RTT_30}
 			\label{fig:3.3d}

### 2017-12-20 paper-tex/paper.tex
modifying

--- 2017-12-20 paper-tex/paper.tex
@@
 Here we do not provide strict proofs of the temporal dependencies that lie in these routes but simply throw some light on the possibility of their existence.
+	\begin{figure*} 	
+		\includegraphics[width=0.22\textwidth]{fig/total_life_8} 
+		\label{fig:3.1a}
+		\includegraphics[width=0.22\textwidth]{fig/total_life_20}
+		\label{fig:3.1b}
+		\includegraphics[width=0.22\textwidth]{fig/total_life_21}
+		\label{fig:3.1c}
+		\includegraphics[width=0.22\textwidth]{fig/total_life_30}
+		\label{fig:3.1d}
 
-	\begin{figure}[tp]
-		\centering
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_8}
-			\label{fig:3.1a}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_20}
-			\label{fig:3.1b}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_21}
-			\label{fig:3.1c}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_30}
-			\label{fig:3.1d}
-		\end{subfigure}
+		%\vspace{-20pt}  
 		\caption{Temporal patterns of route life among 4 different paths.}
 		\label{fig:3.1}  
-	\end{figure}
+		%\vspace{-10pt}  
+	\end{figure*}
 
-	\begin{figure}[!htp]
-		\centering
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_8}
+\begin{figure*} 	
+	\includegraphics[width=0.22\textwidth]{fig/route_change_8} 
 	\label{fig:3.2a}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_20}
+	\includegraphics[width=0.22\textwidth]{fig/route_change_20}
 	\label{fig:3.2b}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_21}
+	\includegraphics[width=0.22\textwidth]{fig/route_change_21}
 	\label{fig:3.2c}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_30}
+	\includegraphics[width=0.22\textwidth]{fig/route_change_30}
 	\label{fig:3.2d}
-		\end{subfigure}
+
+	%\vspace{-20pt}  
 	\caption{Temporal patterns of the number of route changes among 4 different paths.}
 	\label{fig:3.2}  
-	\end{figure}
+	%\vspace{-10pt}  
+\end{figure*}
 
-	\begin{figure}[!htp]
-		\centering
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_8}
+\begin{figure*} 	
+	\includegraphics[width=0.22\textwidth]{fig/RTT_8} 
 	\label{fig:3.3a}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_20}
+	\includegraphics[width=0.22\textwidth]{fig/RTT_20}
 	\label{fig:3.3b}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_21}
+	\includegraphics[width=0.22\textwidth]{fig/RTT_21}
 	\label{fig:3.3c}
-		\end{subfigure}
-		\begin{subfigure}[t]{0.4\linewidth}
-			\centering
-			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_30}
+	\includegraphics[width=0.22\textwidth]{fig/RTT_30}
 	\label{fig:3.3d}
-		\end{subfigure}
+
+	%\vspace{-20pt}  
 	\caption{Temporal patterns of round trip time among 4 different paths.}
 	\label{fig:3.3}  
-	\end{figure}
+	%\vspace{-10pt}  
+\end{figure*}
 
 	Applying simple differential analysis to the raw data, we found the prediction targets indeed show local temporal patterns which we can hopefully capture with LSTMs.
-Fig.~\ref{fig:3.1} to Fig.~\ref{fig:3.3} exhibit differentiated results of the three prediction targets in different paths.
+\textbf{Fig.\ref{fig:3.1}}, \textbf{Fig.\ref{fig:3.2}} and \textbf{Fig.\ref{fig:3.3}} exhibit differentiated results of the three prediction targets in different paths.
 We can see that these paths behave in somehow consistent temporal patterns along their own ways but differently from each other.
 
-	No more solid evidence could be provided to prove the periodicity of these patterns because \textbf{pattern} itself is hard to define.
+	No more solid evidence could be provided to prove the periodicity of these patterns because pattern itself is hard to define.
 However, these results are already enough to make us hopeful about the performance of LSTMs, which are expert in capturing temporal dependencies, no-matter long-term ones or short-term ones.
@@
 	\subsection{Data Processing}
-	We reprocess the data in several more rational ways, which in other words, predicting targets using the previous information only.
+	We reprocess the data in several more rational ways, which in other words, predicting targets using the previous \texttt{traceroute} data only.
 And to be specific, we divide the data into two sets, namely training set and test set.
 We calculate statistical properties (global features) of paths using three different manners: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ .
-For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th manner ($i$ can be either 1,2 or 3).
-And for the third manner, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
+For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th processing manner ($i$ can be either 1,2 or 3).
+And for the third processing manner, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
 
@@
 In practice, we set $k = 70, 80$ respectively.
-And in the third manner of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
+And in the third processing manner, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
 We find that there is little difference when setting $k$ either to 70 or 80.
@@
 The closer $ABC$ is to $1$, the better prediction result it has.
-These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} and  illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $).
+These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $).
 	\begin{figure*} [!htb] 
@@
 		%\vspace{-20pt}  
-		\caption{Relative prediction errors for $R_r(t)$ using three different data processing manners, and $window\ size$ for the below three figures are 10,20 and 50.}
+		\caption{Relative prediction errors for $R_r(t)$ of random forest models.}
 		\label{fig:task1_RF}  
@@
 		%\vspace{-20pt}  
-		\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing manners, and $window\ size$ for the below three figures are 10,20 and 50.}
+		\caption{Relative prediction errors for $avgRTT_P(t)$ of random forest models.}
 		\label{fig:task3_RF}
@@
 
-	\hui{Note}We first predict the route duration instead of resLife.
-Further study on the difference between these two predicting objective could be conduct if we have time.
-Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
-
-	\subsection{LSTM Model}
-
-	Table 1 describes the $ABC$ in each figure.
+	\textbf{Tab.\ref{tab:result_RF}} describes the $ABC$ of two tasks in different data processing manner.
 	\begin{table}[tbp]
@@
 		\end{tabular}
-		\caption{The $ABC$ of curves
-			in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
+		\caption{Experiment results($ABC$) of random forest models. }
 		\label{tab:result_RF}
 	\end{table}
-	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different manners to process the data.
-They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
+	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference in processing the data in different manners .
+They all achieve relatively good results, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
 However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality.
@@
 And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model.
-Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing manners.
+Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves the largest $ABC$ compared with other processing manners.
 It considers only the recent data in a relatively short time slot.
-Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
-	\subsection{Deep Models}
+Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the recent previous \texttt{traceroute} data).
+	\subsection{LSTM Model}
 
-	As we observed above, among the 3 different \textit{window size} (10, 20, 50), \textit{window size} of 10 alway has the best performance.
+	As we observed above, among the 3 different \textit{window size} (10, 20, 50), \textit{window size} of 10 has the best performance.
 Thus, we set the timesteps for our LSTM model to be 10, either.
-We adopt two kinds of input for the LSTM at each timestep, (i) scalar (ii) vector.
+We adopt two kinds of input for the LSTM at each timestep: $(i)$ scalar and $(ii)$ vector.
+
+	\begin{figure*} 	
+		\includegraphics[width=0.3\textwidth]{fig4/task1-scalar-lstm.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/task3-scalar-lstm.pdf}
+		%\vspace{-20pt}  
+		\caption{Relative prediction errors for $R_r(t)$ and $avgRTT_P(t)$ of LSTM models with scalar input.}
+		\label{fig:task1_LSTM_SC}
+		%\vspace{-10pt}  
+	\end{figure*}
+
 	\subsubsection{Scalar Input}
@@
 		\end{tabular}
-		\caption{ Experiment results of LSTM models with scalar input. }
+		\caption{ Experiment results($ABC$) of LSTM models with scalar input. }
 		\label{tab:lstm-scalar}
@@
 	Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it.
-\textbf{Table \ref{tab:lstm-scalar}} shows the results.
+\textbf{Fig.\ref{fig:task1_LSTM_SC}} and \textbf{Tab.\ref{tab:lstm-scalar}} show the results.
 
-	As we can see, for target $R_r(t)$, the ABC of LSTM is higher than random forest with \textit{data-1} and \textit{data-2}, but is much lower than random forest with \textit{data-3-ws10}.
-This shows empirical evidence that there are temporal locality with $R_r(t)$ of a path.
-We can infer $R_r(t)$ of a path from its recent routes better than using current features only.
+	As we can see, for target $R_r(t)$, the $ABC$ of LSTM is larger	 than random forest with \textit{data-1} and \textit{data-2}, but is much smaller than random forest with \textit{data-3-ws10}.
+This shows empirical evidence that there is temporal locality with $R_r(t)$ of a path.
+We can infer $R_r(t)$ of a path from its recent \texttt{traceroute} measurements better than using current features only.
 

### 2017-12-20 paper-tex/paper.tex
method lstm

--- 2017-12-20 paper-tex/paper.tex
@@
 		\centering
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/total_life_8}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_8}
 			\label{fig:3.1a}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/total_life_20}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_20}
 			\label{fig:3.1b}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/total_life_21}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/total_life_21}
 			\label{fig:3.1c}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/total_life_30}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/total_life_30}
 			\label{fig:3.1d}
@@
 		\centering
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/route_change_8}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_8}
 			\label{fig:3.2a}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/route_change_20}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_20}
 			\label{fig:3.2b}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/route_change_21}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/route_change_21}
 			\label{fig:3.2c}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/route_change_30}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/route_change_30}
 			\label{fig:3.2d}
@@
 		\centering
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/RTT_8}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_8}
 			\label{fig:3.3a}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/RTT_20}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_20}
 			\label{fig:3.3b}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/RTT_21}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip=true]{fig/RTT_21}
 			\label{fig:3.3c}
 		\end{subfigure}
-		\begin{subfigure}[t]{0.45\linewidth}
+		\begin{subfigure}[t]{0.4\linewidth}
 			\centering
-			\includegraphics[width=0.95\linewidth]{fig/RTT_30}
+			\includegraphics[width=0.95\linewidth, trim={100 100 0 0}, clip]{fig/RTT_30}
 			\label{fig:3.3d}
@@
 	\subsection{LSTM Model}
+	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling.
+More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
+	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
+	\begin{equation}
+	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
+	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
+	\begin{equation}
+	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
+	\end{equation}
+	and the loss function is:
+	\begin{equation}
+	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
+	\end{equation}
+	The training objective is to minimize $\mathcal{L}$.
 

### 2017-12-20 paper-tex/paper.tex
check consistency

--- 2017-12-20 paper-tex/paper.tex
@@
 		\caption{Relative prediction errors for $R_r(t)$ and $avgRTT_P(t)$ of LSTM models with scalar input.}
-		\label{fig:task1_LSTM_SC}
+		\label{fig:lstm_scalar}
 		%\vspace{-10pt}  
@@
 	Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it.
-\textbf{Fig.\ref{fig:task1_LSTM_SC}} and \textbf{Tab.\ref{tab:lstm-scalar}} show the results.
+\textbf{Fig.\ref{fig:lstm_scalar}} and \textbf{Tab.\ref{tab:lstm-scalar}} show the results.
 
@@
 
-	To the contrast, for target $avgRTT_P(t)$, the $ABC$ of LSTM is lower than random forest in all cases, which may indicates that $avgRTT_P(t)$ is less likely to have the temporal locality.
+	By contrast, for target $avgRTT_P(t)$, the $ABC$ of LSTM is smaller than random forest in all cases, which may indicate that $avgRTT_P(t)$ is less likely to have the temporal locality.
 
-	For both tasks, use scalar input for LSTM cannot outperform random forest steadily.
+	For both tasks, using scalar input for LSTM cannot outperform random forest steadily.
 
 	\subsubsection{Vector Input}
-	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM as random forest.
-More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
+	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM model as those for random forest model.
+More specifically, Features for target $R_r(t)$ and Features for target $avgRTT_P(t)$.The results are shown in \textbf{Fig.\ref{fig:lstm-task1-vector}}, \textbf{Fig.\ref{fig:lstm-task3-vector}} and \textbf{Tab.\ref{tab:lstm-vector}}.
+
+	\begin{figure*} 	
+		\includegraphics[width=0.3\textwidth]{fig4/data-1-task-1-7030-lstm.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-lstm.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-1-7030-lstm.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-1-7030-lstm.pdf}
+		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-1-7030-lstm.pdf}
+		%\vspace{-20pt}  
+		\caption{Relative prediction errors for $R_r(t)$ of LSTM models with vector input.}
+		\label{fig:lstm-task1-vector}
+		%\vspace{-10pt}  
+	\end{figure*}
+	\begin{figure*} 	
+	\includegraphics[width=0.3\textwidth]{fig4/data-1-task-3-7030-lstm.pdf}
+	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-lstm.pdf}
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-3-7030-lstm.pdf}
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws20-task-3-7030-lstm.pdf}
+	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws50-task-3-7030-lstm.pdf}
+	%\vspace{-20pt}  
+	\caption{Relative prediction errors for  $avgRTT_P(t)$ of LSTM models with vector input.}
+	\label{fig:lstm-task3-vector}
+	%\vspace{-10pt}  
+	\end{figure*}
 	\begin{table}[t]
@@
 
-	In general, the results is consist with our previous observation that $R_r(t)$ has more temporal locality while $avgRTT_p(t)$ seems has few or no temporal locality.
+	In general, the results consist with our previous observation that $R_r(t)$ has more temporal locality while $avgRTT_p(t)$ seems to have less or no temporal locality.
 
-	More specificly, for target $R_r(t)$, LSTM outperforms random forest in all the 5 data set with a maximum $ABC=0.7649$.
-And when fed with vector input, the LSTM has a significant lift in performance than LSTM with scalar input, which shows that high quality features can be benefit to not only classic shadow models like random forest, but also \textit{deep} models.
+	More specifically, for target $R_r(t)$, LSTM model outperforms random forest model in all five data processing manners with a maximum $ABC=0.7649$.
+And when fed with vector input, the LSTM has a significant lift in performance than LSTM with scalar input, which shows that high quality features can be beneficial to not only classic shadow models like random forest, but also \textit{deep} models like LSTM model.
 
-	However, when it comes to target $avgRTT_p(t)$, although LSTM does has better performance when fed with vector input rather than scalar input, its $ABC$ is still lower than random forest's.
-We believe it is because there is less temporal locality with $avgRTT_p(t)$.
-The more data you observed before, the better you can predict $avgRTT_p(t)$ in the future.
+	However, when it comes to target $avgRTT_p(t)$, although LSTM models do have better performance when fed with vector input rather than scalar input, their $ABC$s are still smaller than those of random forest.
+We believe it is because there is less temporal locality with reference to $avgRTT_p(t)$.
+The more data we observed before, the better we can predict $avgRTT_p(t)$ in the future.
 Thus LSTM model cannot maximize its ability in predicting temporal patterns.

### 2017-12-20 paper-tex/paper.tex
To test the bibtex

--- 2017-12-20 paper-tex/paper.tex
@@
 \usepackage{subcaption}
+\usepackage{natbib}
+\usepackage{natbib}
 \newcommand{\kai}[1]{{\bf \color{blue} [[Shukai says ``#1'']]}}
@@
 Here we do not provide strict proofs of the temporal dependencies that lie in these routes but simply throw some light on the possibility of their existence.
-	\begin{figure*} 	
-		\includegraphics[width=0.22\textwidth]{fig/total_life_8} 
+
+	\begin{figure}[tp]
+		\centering
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/total_life_8}
 			\label{fig:3.1a}
-		\includegraphics[width=0.22\textwidth]{fig/total_life_20}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/total_life_20}
 			\label{fig:3.1b}
-		\includegraphics[width=0.22\textwidth]{fig/total_life_21}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/total_life_21}
 			\label{fig:3.1c}
-		\includegraphics[width=0.22\textwidth]{fig/total_life_30}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/total_life_30}
 			\label{fig:3.1d}
-
-		%\vspace{-20pt}  
+		\end{subfigure}
 		\caption{Temporal patterns of route life among 4 different paths.}
 		\label{fig:3.1}
-		%\vspace{-10pt}  
-	\end{figure*}
+	\end{figure}
 
-\begin{figure*} 	
-	\includegraphics[width=0.22\textwidth]{fig/route_change_8} 
+	\begin{figure}[!htp]
+		\centering
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/route_change_8}
 			\label{fig:3.2a}
-	\includegraphics[width=0.22\textwidth]{fig/route_change_20}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/route_change_20}
 			\label{fig:3.2b}
-	\includegraphics[width=0.22\textwidth]{fig/route_change_21}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/route_change_21}
 			\label{fig:3.2c}
-	\includegraphics[width=0.22\textwidth]{fig/route_change_30}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/route_change_30}
 			\label{fig:3.2d}
-
-	%\vspace{-20pt}  
+		\end{subfigure}
 		\caption{Temporal patterns of the number of route changes among 4 different paths.}
 		\label{fig:3.2}
-	%\vspace{-10pt}  
-\end{figure*}
+	\end{figure}
 
-\begin{figure*} 	
-	\includegraphics[width=0.22\textwidth]{fig/RTT_8} 
+	\begin{figure}[!htp]
+		\centering
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/RTT_8}
 			\label{fig:3.3a}
-	\includegraphics[width=0.22\textwidth]{fig/RTT_20}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/RTT_20}
 			\label{fig:3.3b}
-	\includegraphics[width=0.22\textwidth]{fig/RTT_21}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/RTT_21}
 			\label{fig:3.3c}
-	\includegraphics[width=0.22\textwidth]{fig/RTT_30}
+		\end{subfigure}
+		\begin{subfigure}[t]{0.45\linewidth}
+			\centering
+			\includegraphics[width=0.95\linewidth]{fig/RTT_30}
 			\label{fig:3.3d}
-
-	%\vspace{-20pt}  
+		\end{subfigure}
 		\caption{Temporal patterns of round trip time among 4 different paths.}
 		\label{fig:3.3}
-	%\vspace{-10pt}  
-\end{figure*}
+	\end{figure}
 
 	Applying simple differential analysis to the raw data, we found the prediction targets indeed show local temporal patterns which we can hopefully capture with LSTMs.
-\textbf{Fig.\ref{fig:3.1}}, \textbf{Fig.\ref{fig:3.2}} and \textbf{Fig.\ref{fig:3.3}} exhibit differentiated results of the three prediction targets in different paths.
+Fig.~\ref{fig:3.1} to Fig.~\ref{fig:3.3} exhibit differentiated results of the three prediction targets in different paths.
 We can see that these paths behave in somehow consistent temporal patterns along their own ways but differently from each other.
 
-	No more solid evidence could be provided to prove the periodicity of these patterns because pattern itself is hard to define.
+	No more solid evidence could be provided to prove the periodicity of these patterns because \textbf{pattern} itself is hard to define.
 However, these results are already enough to make us hopeful about the performance of LSTMs, which are expert in capturing temporal dependencies, no-matter long-term ones or short-term ones.
@@
 	\subsection{Data Processing}
-	We reprocess the data in several more rational ways, which in other words, predicting targets using the previous \texttt{traceroute} data only.
+	We reprocess the data in several more rational ways, which in other words, predicting targets using the previous information only.
 And to be specific, we divide the data into two sets, namely training set and test set.
 We calculate statistical properties (global features) of paths using three different manners: $(i)$ use the global features (max, min, average, percentiles, etc.) in the training set to get the model and predict the targets of the latter $(1-k)\%$ data, $(ii)$ use the global feature of the former $k\%$ to train the models and update these features during the predicting procedure(i.e.,update the global features everytime there is a new \texttt{traceroute} measurement of a path), and $(iii)$ only use recent \texttt{traceroute} data of certain length (namely $window\ size$) in the training set to calculate the global features, and when using the trained model to predict targets, we only consider features calculated in  recent \texttt{traceroute} measurements of the same $window\ size$ .
-For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th processing manner ($i$ can be either 1,2 or 3).
-And for the third processing manner, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
+For convenience, in the following article, we use $data-i$ to represent reprocessing the original data using the $i$th manner ($i$ can be either 1,2 or 3).
+And for the third manner, we use $data-3-ws\#$ to indicate the $window\ size$ of $\#$.
 
 	\subsection{LSTM Model}
-	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling.
-More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
-	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
-	\begin{equation}
-	\mathbf{h_{i+1}}=G_{\theta}(\mathbf{x_i},\mathbf{h_i}),
-	\end{equation}iteratively. and when we have the $\mathbf{h_{t}}$, we calculate our final prediction $\hat{y}$ by a fully connected layer with parameter $\mathbf{W}$:
-	\begin{equation}
-	\hat{y}=\mathbf{W}\cdot\mathbf{h_t},
-	\end{equation}
-	and the loss function is:
-	\begin{equation}
-	\mathcal{L}=\frac{1}{n}\sum_{i=1}^{n}(y_i-\hat{y_i})^2.
-	\end{equation}
-	The training objective is to minimize $\mathcal{L}$.
 
@@
 In practice, we set $k = 70, 80$ respectively.
-And in the third processing manner, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
+And in the third manner of processing data, the $window\ size$ is set to $10,20$ and $50$ recent \texttt{traceroute} measurements, respectively.
 We find that there is little difference when setting $k$ either to 70 or 80.
@@
 The closer $ABC$ is to $1$, the better prediction result it has.
-These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $).
+These figures in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} and  illustrate the relationship between sample percentage and relative prediction error(i.e., $\mid Real - Predict\mid/ Real $).
 	\begin{figure*} [!htb] 
@@
 		%\vspace{-20pt}  
-		\caption{Relative prediction errors for $R_r(t)$ of random forest models.}
+		\caption{Relative prediction errors for $R_r(t)$ using three different data processing manners, and $window\ size$ for the below three figures are 10,20 and 50.}
 		\label{fig:task1_RF}  
@@
 		%\vspace{-20pt}  
-		\caption{Relative prediction errors for $avgRTT_P(t)$ of random forest models.}
+		\caption{Relative prediction errors for $avgRTT_P(t)$ using three different data processing manners, and $window\ size$ for the below three figures are 10,20 and 50.}
 		\label{fig:task3_RF}
@@
 
-	\textbf{Tab.\ref{tab:result_RF}} describes the $ABC$ of two tasks in different data processing manner.
+	\hui{Note}We first predict the route duration instead of resLife.
+Further study on the difference between these two predicting objective could be conduct if we have time.
+Currently, we predict the route duration for task 1, because we can only predict this when we use LSTM.
+
+	\subsection{LSTM Model}
+
+	Table 1 describes the $ABC$ in each figure.
 	\begin{table}[tbp]
@@
 		\end{tabular}
-		\caption{Experiment results($ABC$) of random forest models. }
+		\caption{The $ABC$ of curves
+			in \textbf{Fig.\ref{fig:task1_RF}} and \textbf{Fig.\ref{fig:task3_RF}} }
 		\label{tab:result_RF}
 	\end{table}
-	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference in processing the data in different manners .
-They all achieve relatively good results, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
+	From \textbf{Tab.\ref{tab:result_RF}}, it can be inferred that for target $avgRTT_P(t)$: there is minor difference using five different manners to process the data.
+They all achieve a relatively good result, which also indicates that for average RTT reported from \texttt{traceroute} measurement, it is not sensitive to the temporal locality.
 However, for the first predicting target, $R_r(t)$, it is very sensitive to the temporal locality.
@@
 And to achieve better prediction result, using too much previous data will result in noise and decrease the performance of the model.
-Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves the largest $ABC$ compared with other processing manners.
+Because from \textbf{Tab.\ref{tab:result_RF}}, we can clearly observe that $data-3-ws10$ achieves larget $ABC$ compared with other processing manners.
 It considers only the recent data in a relatively short time slot.
-Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the recent previous \texttt{traceroute} data).
-	\subsection{LSTM Model}
+Indeed, it is reasonable to get such conclusion, for the remaining life time of a route is always closely related to their route age (which can be indicated from the previous \texttt{traceroute} data).
+	\subsection{Deep Models}
 
-	As we observed above, among the 3 different \textit{window size} (10, 20, 50), \textit{window size} of 10 has the best performance.
+	As we observed above, among the 3 different \textit{window size} (10, 20, 50), \textit{window size} of 10 alway has the best performance.
 Thus, we set the timesteps for our LSTM model to be 10, either.
-We adopt two kinds of input for the LSTM at each timestep: $(i)$ scalar and $(ii)$ vector.
-
-	\begin{figure*} 	
-		\includegraphics[width=0.3\textwidth]{fig4/task1-scalar-lstm.pdf}
-		\includegraphics[width=0.3\textwidth]{fig4/task3-scalar-lstm.pdf}
-		%\vspace{-20pt}  
-		\caption{Relative prediction errors for $R_r(t)$ and $avgRTT_P(t)$ of LSTM models with scalar input.}
-		\label{fig:task1_LSTM_SC}
-		%\vspace{-10pt}  
-	\end{figure*}
-
+We adopt two kinds of input for the LSTM at each timestep, (i) scalar (ii) vector.
 	\subsubsection{Scalar Input}
@@
 		\end{tabular}
-		\caption{ Experiment results($ABC$) of LSTM models with scalar input. }
+		\caption{ Experiment results of LSTM models with scalar input. }
 		\label{tab:lstm-scalar}
@@
 	Since we have observed some local temporal patterns with the prediction targets, The most naive approach is to feed LSTM with the previous observed scalar without any statistics of it.
-\textbf{Fig.\ref{fig:task1_LSTM_SC}} and \textbf{Tab.\ref{tab:lstm-scalar}} show the results.
+\textbf{Table \ref{tab:lstm-scalar}} shows the results.
 
-	As we can see, for target $R_r(t)$, the $ABC$ of LSTM is larger	 than random forest with \textit{data-1} and \textit{data-2}, but is much smaller than random forest with \textit{data-3-ws10}.
-This shows empirical evidence that there is temporal locality with $R_r(t)$ of a path.
-We can infer $R_r(t)$ of a path from its recent \texttt{traceroute} measurements better than using current features only.
+	As we can see, for target $R_r(t)$, the ABC of LSTM is higher than random forest with \textit{data-1} and \textit{data-2}, but is much lower than random forest with \textit{data-3-ws10}.
+This shows empirical evidence that there are temporal locality with $R_r(t)$ of a path.
+We can infer $R_r(t)$ of a path from its recent routes better than using current features only.
 
@@
 More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
-	\begin{table}[t]
+	\begin{table}[htp]
 		\centering
@@
 	\bibliographystyle{ACM-Reference-Format}
-	\bibliography{bibliography}
+	\bibliography{test-bib}
 

### 2017-12-20 paper-tex/paper.tex
minor

--- 2017-12-20 paper-tex/paper.tex
@@
 
-	\subsection{LSTM Model}
-	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling.
+	\subsection{Long Short-Term Memory}
+	In order to leverage the prediction targets' character of temporal locality, we further use Long Short-Term Memory (LSTM) to do time series modeling.
 More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.

### 2017-12-20 paper-tex/paper.tex
small modification

--- 2017-12-20 paper-tex/paper.tex
@@
 	In order to leverage the prediction targets' character of temporal locality, we further use LSTM to do time series modeling.
-More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
+More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input, i.e., $\mathbf{X}=(\mathbf{x_1}, \mathbf{x_2},...,\mathbf{x_{t-1}}, \mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
 	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
@@
 			Target &$R_r(t)$ &$avgRTT_P(t)$ \\ \hline
-			$data-1$ & 0.4016    &0.8124   \\        
-			$data-2$ &0.3985 &0.8261 \\        
-			$data-3-ws10$  &0.7132 &0.8018 \\
-			$data-3-ws20$ &0.6314 &0.7910 \\
-			$data-3-ws50$ &0.5359  &0.7790 \\ \hline
+			\textit{data-1} & 0.4016    &0.8124   \\        
+			\textit{data-2} &0.3985 &0.8261 \\        
+			\textit{data-3-ws10}  &0.7132 &0.8018 \\
+			\textit{data-3-ws20} &0.6314 &0.7910 \\
+			\textit{data-3-ws50} &0.5359  &0.7790 \\ \hline
 		\end{tabular}
@@
 		\includegraphics[width=0.3\textwidth]{fig4/data-2-task-1-7030-lstm.pdf}
+	\end{figure*} 
+	\begin{figure*} 
 		\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-1-7030-lstm.pdf}
@@
 	\includegraphics[width=0.3\textwidth]{fig4/data-2-task-3-7030-lstm.pdf}
+	\end{figure*} 
+	\begin{figure*} 	
 	\includegraphics[width=0.3\textwidth]{fig4/data-3-ws10-task-3-7030-lstm.pdf}

### 2017-12-20 paper-tex/paper.tex
strange commit

--- 2017-12-20 paper-tex/paper.tex
@@
 	\subsubsection{Scalar Input}
-	\begin{table}[t]
+	\begin{table}[tbp]
 		\centering
@@
 	\subsubsection{Vector Input}
+	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM as random forest.
+More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
+
 	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM model as those for random forest model.
@@
 	\end{figure*}
-	\begin{table}[t]
+	\begin{table}[tbp]
 		\centering

### 2017-12-20 paper-tex/paper.tex
abs and conclusion

--- 2017-12-20 paper-tex/paper.tex
@@
 	}
-	\email{felixwzh@outlook.com}
+	\email{felixwzh@sjtu.edu.cn}
 
@@
 	}
-	\email{?@?.com}
+	\email{wrystal@sjtu.edu.cn}
 
@@
 	}
-	\email{?@?.com}
+	\email{zyh1996@sjtu.edu.cn}
 
@@
 	}
-	\email{?@?.com}
+	\email{83558399@qq.com}
 
@@
 	\begin{abstract}
-		We study the problem of predicting internet path dynamics and performance. We use \texttt{traceroute} measurement and machine learning models.
+		We study the problem of predicting internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
+In this work, we first ponit out the drawbacks of the data processing of one previous work \cite{}, and reprocess the data in several more rational ways.
+We then conduct the experiments on the reprocessed data with random forest model.
+With
+		the data analysis and experiment results' insights, we furthe leverage Long Short-Term Memory (LSTM), one kind of recurrent neural network (RNN), and get promissing results.
+We make our reprocessed data and experiment code publicly available\footnote{{https://github.com/felixwzh/CN-group-project}}.
 	\end{abstract}
@@
 
-	\keywords{TODO}
+	%\keywords{TODO}
 
@@
 
-	\hui{I think we should focus on the process not the final result, which is also important.}
+	%\hui{I think we should focus on the process not the final result, which is also important.}
 
@@
 	\section{Conclusions}
-	TODO
+	In this paper, We study the problem of predicting internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
+We reprocess one dataset in several more rational ways and conduct extensive experiments on the reprocessed dataset with random forest and LSTM model.
+We find that some features e.g., $R_r(t)$, is more likely to have temporal locality than other features like $avgRTT_p(t)$, and this insight can guide us to select the most suitable model facing such tasks in computer network scenarios.
 
-	\begin{acks}
-		TODO
-	\end{acks}
+	%\begin{acks}
+	%	TODO
+	%\end{acks}
 

### 2017-12-20 paper-tex/paper.tex
Reference fixed.
minor mistake

@@
 	\begin{abstract}
-		We study the problem of predicting internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
-In this work, we first ponit out the drawbacks of the data processing of one previous work \cite{}, and reprocess the data in several more rational ways.
+		We study the problem of predicting Internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
+In this work, we first point out the drawbacks of the data processing in one previous work \cite{}, and reprocess the data in several more rational ways.
 We then conduct the experiments on the reprocessed data with random forest model.
 With
-		the data analysis and experiment results' insights, we furthe leverage Long Short-Term Memory (LSTM), one kind of recurrent neural network (RNN), and get promissing results.
+		the data analysis and experiment results' insights, we further leverage Long Short-Term Memory (LSTM) model, one kind of recurrent neural network (RNN), and get promising results.
 We make our reprocessed data and experiment code publicly available\footnote{{https://github.com/felixwzh/CN-group-project}}.
@@
 More specifically, Features for target $R_r(t)$ and Features for target $avgRTT_P(t)$.The results are shown in \textbf{Fig.\ref{fig:lstm-task1-vector}}, \textbf{Fig.\ref{fig:lstm-task3-vector}} and \textbf{Tab.\ref{tab:lstm-vector}}.
-
+	\begin{table}[tbp]
+		\centering
+		\begin{tabular}{lcc}
+			\toprule
+			{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
+			\midrule
+			\textit{data-1}& 0.5374 & 0.7310 \\
+			\textit{data-2}& 0.4956& 0.7039     \\
+			\textit{data-3-ws10}& 0.7649 & 0.7521 \\
+			\textit{data-3-ws20}& 0.6513& 0.6901    \\
+			\textit{data-3-ws50}& 0.5647& 0.7074  \\
+			\bottomrule	
+		\end{tabular}
+		\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
+		\label{tab:lstm-vector}
+	\end{table}
 	\begin{figure*} 	
@@
 	\end{figure*}
-	\begin{table}[tbp]
-		\centering
-		\begin{tabular}{lcc}
-			\toprule
-			{Target} &{$R_r(t)$}&{$avgRTT_p(t)$} \\
-			\midrule
-			\textit{data-1}& 0.5374 & 0.7310 \\
-			\textit{data-2}& 0.4956& 0.7039     \\
-			\textit{data-3-ws10}& 0.7649 & 0.7521 \\
-			\textit{data-3-ws20}& 0.6513& 0.6901    \\
-			\textit{data-3-ws50}& 0.5647& 0.7074  \\
-			\bottomrule	
-		\end{tabular}
-		\caption{ Experiment results ($ABC$) of LSTM models with vector input. }
-		\label{tab:lstm-vector}
-	\end{table}
 

### 2017-12-20 paper-tex/paper.tex
add lstm fig

@@
 Here we do not provide strict proofs of the temporal dependencies that lie in these routes but simply throw some light on the possibility of their existence.
+	\begin{figure}[t] 
+		\includegraphics[width=0.3\textwidth]{fig/lstm.pdf} 
+		\caption{Illustration for LSTM.} 
+		\label{fig:lstm} 
+	\end{figure}
 	\begin{figure*} 	
@@
 	\subsection{Long Short-Term Memory}
+
 	In order to leverage the prediction targets' character of temporal locality, we further use Long Short-Term Memory (LSTM) to do time series modeling.
@@
 	\end{equation}
-	The training objective is to minimize $\mathcal{L}$.
+	The training objective is to minimize $\mathcal{L}$. The LSTM we adopt is illustrated in \textbf{Fig.\ref{fig:lstm}}
 
@@
 
-	%\begin{acks}
-	%	TODO
-	%\end{acks}
+	\begin{acks}
+		TODO
+	\end{acks}
 
 	\bibliographystyle{ACM-Reference-Format}
-	\bibliography{test-bib}
+	\bibliography{bibliography}
 

### 2017-12-20 paper-tex/paper.tex
minor

@@
 	\label{sec:dataAna}
-	\hui{I think this is an important part, who will take this part?}
-	\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
+	%\hui{I think this is an important part, who will take this part?}
+	%\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
 	With careful review of the data used in the original paper, here we: $(i)$ show the authors had used the data incorrectly in the context of making predictions, and $(ii)$ reveal the temporal properties that the original method failed to employ but perfectly fits LSTM model (long short term memory neural networks), which we will later use to improve the performance.

### 2017-12-20 paper-tex/paper.tex
Minor corrections and abstract fine-tuning.

--- 2017-12-20 paper-tex/paper.tex
@@
 		We study the problem of predicting Internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
-In this work, we first point out the drawbacks of the data processing in one previous work \cite{}, and reprocess the data in several more rational ways.
-We then conduct the experiments on the reprocessed data with random forest model.
-With
-		the data analysis and experiment results' insights, we further leverage Long Short-Term Memory (LSTM) model, one kind of recurrent neural network (RNN), and get promising results.
+In this work, we first point out the drawbacks of the data processing in one previous work \cite{wassermann2017predicting}, and reprocess the data in several more rational ways.
+Then data analysis and experiments are conducted on the reprocessed data with random forest model before evident temporal locality is discovered in the behavior of the paths.
+Inspired by this property, we further leverage Long Short-Term Memory (LSTM) model, one kind of recurrent neural networks (RNN), and get promising results.
 We make our reprocessed data and experiment code publicly available\footnote{{https://github.com/felixwzh/CN-group-project}}.
@@
 	\section{Introduction}
-	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures\cite{1}.
+	Internet paths change frequently due to inter/intra-domain routing changes, load balancing, and even misconfigurations and failures\cite{paxson1996end}.
 	%  V. Paxson. 1996. End-to-end Routing Behavior in the Internet. In Proceedings of the ACM SIGCOMM 1996 Conference (SIGCOMM ’96). ACM, New York, NY, USA.
-	Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity\cite{2}.
+	Some of these changes can seriously disrupt performance, causing longer round-trip times, congestion, or even loss of connectivity\cite{javed2013poiroot}.
 	%U.
@@
 
-	In the original paper\cite{oripaper}, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
+	In the original paper\cite{wassermann2017predicting}, the authors focus on the problem of predicting Internet path changes and path performance using \texttt{traceroute} measurements.
 They use the recent route information of paths (route age for paths, route changes in the past, average RTT, etc) to do some predictions of paths.
@@
 And only 2,346 paths have at least 100 \texttt{traceroute} measurements during the analyzed week.
-So the dataset contains corresponding infomation of these 2,346 paths.
+So the dataset contains corresponding information of these 2,346 paths.
 
-	We find some drawbacks in their data process.(see section \ref{sec:dataAna}) And in our own work, firstly we reprocess the provided data in more resonable ways and use the same method (random forest model) mentioned by the original paper\cite{oripaper} to compare the results.
+	We find some drawbacks in their data process.(see section \ref{sec:dataAna}) And in our own work, firstly we reprocess the provided data in more reasonable ways and use the same method (random forest model) mentioned by the original paper\cite{wassermann2017predicting} to compare the results.
 Secondly, another machine learning method, LSTM model, is applied to get better performance.
@@
 	\section{Related Works}
-	In the original paper\cite{oripaper}, the problem they solve is to use random forest model to predict three targets for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T(t)$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.
+	In the original paper\cite{wassermann2017predicting}, the problem they solve is to use random forest model to predict three targets for one path: $(i)$ the remaining life time of a route for one path at time $t$ (i.e., the time before a route changes), namely $R_r(t)$, $(ii)$ the number of route changes for one path $P$ in a future timeslot $T$, namely $rcP_T(t)$  and $(iii)$ the average RTT that the path $P$ will experience in the next \texttt{traceroute} measurement, namely $avgRTT_P(t)$.
 
@@
 
-	And the last group of 44 features ,referred to as $F_C$ decribes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement.
-They calculate the staistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
+	And the last group of 44 features ,referred to as $F_C$ describes statistical properties of path latency, which is relavent to the prediction of the next \texttt{traceroute} measurement.
+They calculate the statistical properties of four RTT metrics (average, minimum, maximum and standard deviation) reported from each \texttt{traceroute} measurement.
 
@@
 	\label{sec:dataAna}
-	\hui{I think this is an important part, who will take this part?}
-	\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
 	With careful review of the data used in the original paper, here we: $(i)$ show the authors had used the data incorrectly in the context of making predictions, and $(ii)$ reveal the temporal properties that the original method failed to employ but perfectly fits LSTM model (long short term memory neural networks), which we will later use to improve the performance.
 	\subsection{Justification of Data Processing}
-	The original paper \cite{oripaper} made a major mistake on data employment: they implicitly used data from the future to predict events in the future, which is not possible.
+	The original paper \cite{wassermann2017predicting} made a major mistake on data employment: they implicitly used data from the future to predict events in the future, which is not possible.
 More specifically, all of their tests on the performance of \textit{NetPerfTrace} depend on statistics calculated out of data of all time, including the data they were to predict.
@@
 	No more solid evidence could be provided to prove the periodicity of these patterns because pattern itself is hard to define.
-However, these results are already enough to make us hopeful about the performance of LSTMs, which are expert in capturing temporal dependencies, no-matter long-term ones or short-term ones.
+However, these results are already enough to make us hopeful about the performance of LSTM, which are expert in capturing temporal dependencies, no-matter long-term ones or short-term ones.
 
@@
 	In order to leverage the prediction targets' character of temporal locality, we further use Long Short-Term Memory (LSTM) to do time series modeling.
-More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input,i.e.,$\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$ And the out put is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
+More formally, we take $t-1$ most recent \texttt{traceroute} measurements features $(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-2}},\mathbf{x_{t-1}})$and the current \texttt{traceroute} measurement feature $\mathbf{x_t}$ together as the input, i.e., $\mathbf{X}=(\mathbf{x_1},\mathbf{x_2},...,\mathbf{x_{t-1}},\mathbf{x_{t}})$.
+And the output is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
 	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
@@
 	\subsubsection{Vector Input}
-	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM as random forest.
+	%In order to better leverage the data to get better performance with our LSTM model, we take the same features for LSTM as random forest.
 More specifically, $F_A$ for target $R_r(t)$ and $F_C$ for target $avgRTT_P(t)$.The results are are shown in \textbf{Table~\ref{tab:lstm-vector}}.
@@
 	In order to better leverage the data to get better performance with our LSTM model, we take the same featues for LSTM model as those for random forest model.
-More specifically, Features for target $R_r(t)$ and Features for target $avgRTT_P(t)$.The results are shown in \textbf{Fig.\ref{fig:lstm-task1-vector}}, \textbf{Fig.\ref{fig:lstm-task3-vector}} and \textbf{Tab.\ref{tab:lstm-vector}}.
+More specifically, Features for target $R_r(t)$ and features for target $avgRTT_P(t)$.
+The results are shown in \textbf{Fig.\ref{fig:lstm-task1-vector}}, \textbf{Fig.\ref{fig:lstm-task3-vector}} and \textbf{Tab.\ref{tab:lstm-vector}}.
 	\begin{table}[tbp]
@@
 	\section{Conclusions}
-	In this paper, We study the problem of predicting internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
+	In this paper, we study the problem of predicting Internet path dynamics and performance with \texttt{traceroute} measurement and machine learning models.
 We reprocess one dataset in several more rational ways and conduct extensive experiments on the reprocessed dataset with random forest and LSTM model.
-We find that some features e.g., $R_r(t)$, is more likely to have temporal locality than other features like $avgRTT_p(t)$, and this insight can guide us to select the most suitable model facing such tasks in computer network scenarios.
+It is found that some features, e.g., $R_r(t)$, are more likely to have temporal locality than other features like $avgRTT_p(t)$, and this insight can guide us to select the most suitable model facing such tasks in computer network scenarios.
 
-	%\begin{acks}
-	%	TODO
-	%\end{acks}
+	\begin{acks}
+	This work is successfully produced thanks to the kind guidance from and discussion with Prof.
+Linghe Kong.
+His revealed us common shortcomings of ML-CN works and inspired us to build models that suits \emph{network} better.
+	\end{acks}
 
+	{\small
 		\bibliographystyle{ACM-Reference-Format}
-	\bibliography{test-bib}
+		\bibliography{bibliography} 	
+	}
 

### 2017-12-20 paper-tex/paper.tex

@@
 	\label{sec:dataAna}
+	%\hui{I think this is an important part, who will take this part?}
+	%\heng{Plots of temporally differentiated prediction targets are given here to show their behavior patterns in temporal domain, thus supporting the use of LSTMs.}
 	With careful review of the data used in the original paper, here we: $(i)$ show the authors had used the data incorrectly in the context of making predictions, and $(ii)$ reveal the temporal properties that the original method failed to employ but perfectly fits LSTM model (long short term memory neural networks), which we will later use to improve the performance.
@@
 And the output is a single scalar $\hat{y}$ which is supposed to be the prediction of the target $y$.
+
 	Let $G_{\theta}(\mathbf{x_i},\mathbf{h_i})$ the $\theta$ parameterized LSTM, we have:
